---
title: "2_fig_2_to_4"
author: "Prashant Garg"
date: "2024-06-07"
output: html_document
---
# Goal: create Figures 2 to 4, and Extended Data Figures 2 to 4

----------------------------------------------------------------------


# Layperson Explanation:
Load Data: The script starts by loading datasets from CSV files into dataframes.
Prepare Variables and Names: It defines lists and mappings for variables and their labels.
Function to Calculate Statistics: A function is defined to calculate mean, standard error, and confidence intervals.
Main Figures: The script calculates statistics and creates plots for different groups of variables (climate, economic, behavioral). Each figure involves similar steps: calculating stats for different subgroups, labeling variables, and plotting data.
Extended Data Figures: Similar to the main figures, but with additional normalization relative to the US general population.
Save Plots: Optionally save the plots as high-resolution images.

-----------------------------------------------------------------------

# Pseudocode:

# Load Data
LOAD datasets 'repl_df.csv' and 'users_df.csv' into dataframes 'repl_df' and 'users_df'

# Prepare Variables and Names
DEFINE variable list 'variables' for analysis
DEFINE mapping 'topic_label_mapping' for variable labels

DEFINE groups of variables 'clim_var', 'econ_var', 'beh_var' for different analysis sections

# Function to Calculate Statistics
DEFINE function 'calculate_stats' to calculate mean, standard error, and confidence intervals for a given data column

# Main Figures

## Figure 2: Climate Variables
FOR each variable in 'clim_var'
    CALCULATE stats for the whole dataset, females, males, STEM, social sciences, humanities
    CALCULATE stats for high and low reach and expertise in climate, top and non-top 100 universities, US and non-US
    CALCULATE stats for climate experts and non-experts
    COMBINE results into dataframes for field, reach by expertise, gender, rank, and country groups

    LABEL variables and ensure correct factor levels
    ADD main mean for each label
    PLOT data with ggplot, including points and error bars, faceted by group and label

## Figure 3: Economic Variables
FOR each variable in 'econ_var'
    REPEAT the above steps for calculating stats and plotting
    CALCULATE stats for high and low reach and expertise in economy and culture

## Figure 4: Behavioral Variables
FOR each variable in 'beh_var'
    REPEAT the above steps for calculating stats and plotting
    CALCULATE stats for high and low reach and credibility

# Extended Data Figures

## Extended Data Figure 2: Climate Variables
FOR each variable in 'clim_var'
    CALCULATE stats as for Figure 2
    CALCULATE stats for US users
    NORMALIZE values relative to US general population
    PLOT data with ggplot, faceted by group and label

## Extended Data Figure 3: Economic Variables
FOR each variable in 'econ_var'
    CALCULATE stats as for Figure 3
    CALCULATE stats for US users
    NORMALIZE values relative to US general population
    PLOT data with ggplot, faceted by group and label

## Extended Data Figure 4: Behavioral Variables
FOR each variable in 'beh_var'
    CALCULATE stats as for Figure 4
    CALCULATE stats for US users
    NORMALIZE values relative to US general population
    PLOT data with ggplot, faceted by group and label

# Save Plots
OPTIONALLY save each plot as a high-resolution image file

# Conducts Statistical Tests and Provides Wide Range of Evidence for Statistical Reporting
----------------------------------------------------------------------



# data
```{r}
repl_df <- read_csv( "../2_data/repl_df.csv")
users_df <- read_csv( "../2_data/users_df.csv")
```



# prep
variables and names
```{r}
variables <- c("egocentrism", "toxicity", "emotionality", "stance_climate_action", "pro_techno_prop", "pro_beh_prop",  "stance_econ_collectivism", "stance_cultural_liberalism") 

topic_label_mapping <- c(
  "egocentrism" = "Egocentrism",
  "toxicity" = "Toxicity",
  "emotionality" = "Emotionality/Reasoning",
  "stance_climate_action" = "Climate Action",
  "pro_techno_prop" = "Techno-Optimism",
  "pro_beh_prop" = "Behavioural Adjustment",
  "stance_econ_collectivism" = "Economic Collectivism",
  "stance_cultural_liberalism" = "Cultural Liberalism"
)

clim_var <- c("pro_techno_prop", "pro_beh_prop", "stance_climate_action")
econ_var <- c("stance_cultural_liberalism",  "stance_econ_collectivism")
beh_var <- c("emotionality", "toxicity",  "egocentrism")
```

function to calc
```{r}
# Function to calculate mean, standard error, and confidence intervals for given data column
calculate_stats <- function(data, var_name) {
  var_data <- na.omit(data[[var_name]])  # Remove NA values
  n <- length(var_data)
  mean_val <- mean(var_data)
  std_error <- sd(var_data) / sqrt(n)
  z <- qnorm(0.975)  # 95% CI
  ci_lower <- mean_val - z * std_error
  ci_upper <- mean_val + z * std_error
  
  data.frame(
    Term = var_name,
    Mean = mean_val,
    StdError = std_error,
    CI_lower = ci_lower,
    CI_upper = ci_upper
  )
}
```

# Main Figures
Figure 2
```{r}
# Map the function over each variable group and combine results
stats_pol_main <- map_df(clim_var, ~calculate_stats(repl_df, .x))

stats_pol_is_female <- map_df(clim_var, ~calculate_stats(repl_df %>% filter(is_female==1), .x))
stats_pol_is_male <- map_df(clim_var, ~calculate_stats(repl_df %>% filter(is_male==1), .x))

stats_pol_is_stem <- map_df(clim_var, ~calculate_stats(repl_df %>% filter(is_stem==1), .x))
stats_pol_is_soc_sci <- map_df(clim_var, ~calculate_stats(repl_df %>% filter(is_soc_sci==1), .x))
stats_pol_is_humanities <- map_df(clim_var, ~calculate_stats(repl_df %>% filter(is_humanities==1), .x))

stats_pol_type_H_reach_H_exp_climate <- map_df(clim_var, ~calculate_stats(repl_df %>% filter(type_H_reach_H_exp_climate==1), .x))
stats_pol_type_H_reach_L_exp_climate <- map_df(clim_var, ~calculate_stats(repl_df %>% filter(type_H_reach_L_exp_climate==1), .x))
stats_pol_type_L_reach_H_exp_climate <- map_df(clim_var, ~calculate_stats(repl_df %>% filter(type_L_reach_H_exp_climate==1), .x))
stats_pol_type_L_reach_L_exp_climate <- map_df(clim_var, ~calculate_stats(repl_df %>% filter(type_L_reach_L_exp_climate==1), .x))

stats_pol_ranking_1_100 <- map_df(clim_var, ~calculate_stats(repl_df %>% filter(ranking_cat == "1-100"), .x))
stats_pol_ranking_1_100$Type <- "1-100"

stats_pol_ranking_101_500 <- map_df(clim_var, ~calculate_stats(repl_df %>% filter(ranking_cat == "101-500"), .x))
stats_pol_ranking_101_500$Type <- "101-500"

stats_pol_ranking_501_1500 <- map_df(clim_var, ~calculate_stats(repl_df %>% filter(ranking_cat == "501-1500"), .x))
stats_pol_ranking_501_1500$Type <- "501-1500"

stats_pol_ranking_1501 <- map_df(clim_var, ~calculate_stats(repl_df %>% filter(ranking_cat == "1501+"), .x))
stats_pol_ranking_1501$Type <- "1501+"

stats_pol_is_US <- map_df(clim_var, ~calculate_stats(repl_df %>% filter(is_US==1), .x))
stats_pol_isnt_US <- map_df(clim_var, ~calculate_stats(repl_df %>% filter(is_US==0), .x))

stats_pol_is_climate_expert <- map_df(clim_var, ~calculate_stats(repl_df %>% filter(is_climate_expert==1), .x))
stats_pol_does_do_climate <- map_df(clim_var, ~calculate_stats(repl_df %>% filter(is_climate_expert==0), .x))

stats_pol_field <- bind_rows(
  mutate(stats_pol_is_humanities, Type = "Humanities"),
  mutate(stats_pol_is_soc_sci, Type = "Soc. Sciences"),
  mutate(stats_pol_is_stem, Type = "STEM")
)
stats_pol_field$Type <- factor(stats_pol_field$Type, levels = c("Humanities", "Soc. Sciences", "STEM"))

stats_pol_reach_by_exp_climate <- bind_rows(
  mutate(stats_pol_type_H_reach_H_exp_climate, Type = "High R-E"),
  mutate(stats_pol_type_H_reach_L_exp_climate, Type = "High R-Not E"),
  mutate(stats_pol_type_L_reach_H_exp_climate, Type = "Low R-E"),
  mutate(stats_pol_type_L_reach_L_exp_climate, Type = "Low R-Not E")
)
stats_pol_reach_by_exp_climate$Type <- factor(stats_pol_reach_by_exp_climate$Type, levels = c("High R-E", "High R-Not E", "Low R-E", "Low R-Not E"))

stats_pol_gender <- bind_rows(
  mutate(stats_pol_is_female, Type = "Female"),
  mutate(stats_pol_is_male, Type = "Male")
)
stats_pol_gender$Type <- factor(stats_pol_gender$Type, levels = c("Female", "Male"))

stats_pol_rank <- bind_rows(
  stats_pol_ranking_1_100,
  stats_pol_ranking_101_500,
  stats_pol_ranking_501_1500,
  stats_pol_ranking_1501
)
stats_pol_rank$Type <- factor(stats_pol_rank$Type, levels = c("1-100", "101-500", "501-1500", "1501+"))

stats_pol_US <- bind_rows(
  mutate(stats_pol_is_US, Type = "US"),
  mutate(stats_pol_isnt_US, Type = "Non-US")
)
stats_pol_US$Type <- factor(stats_pol_US$Type, levels = c("US", "Non-US"))

stats_pol_main$Type <- "Main"
stats_pol_main$Type <- factor(stats_pol_main$Type, levels = "Main")

stats_pol_main$Label <- factor(stats_pol_main$Term, levels = clim_var, labels = topic_label_mapping[clim_var])
stats_pol_field$Label <- factor(stats_pol_field$Term, levels = clim_var, labels = topic_label_mapping[clim_var])
stats_pol_reach_by_exp_climate$Label <- factor(stats_pol_reach_by_exp_climate$Term, levels = clim_var, labels = topic_label_mapping[clim_var])
stats_pol_gender$Label <- factor(stats_pol_gender$Term, levels = clim_var, labels = topic_label_mapping[clim_var])
stats_pol_rank$Label <- factor(stats_pol_rank$Term, levels = clim_var, labels = topic_label_mapping[clim_var])
stats_pol_US$Label <- factor(stats_pol_US$Term, levels = clim_var, labels = topic_label_mapping[clim_var])

stats_pol_comb <- bind_rows(stats_pol_main, stats_pol_field, stats_pol_reach_by_exp_climate, stats_pol_gender, stats_pol_rank, stats_pol_US)

stats_pol_comb$Group <- with(stats_pol_comb, case_when(
  Type %in% c("Main") ~ "Main",
  Type %in% c("Female", "Male") ~ "Gender",
  Type %in% c("STEM", "Soc. Sciences", "Humanities") ~ "Fields",
  Type %in% c("High R-E", "High R-Not E", "Low R-E", "Low R-Not E") ~ "Reach (R) by Expertise (E)",
  Type %in% c("1-100", "101-500", "501-1500", "1501+") ~ "University Rankings",
  Type %in% c("US", "Non-US") ~ "Country"
))
stats_pol_comb$Group <- factor(
  stats_pol_comb$Group,
  levels = c(
    "Main", 
    "Gender",
    "Fields",
    "Reach (R) by Expertise (E)",
    "University Rankings",
    "Country"
  )
)

# Ensure 'Type' has a proper order that reflects groupings
stats_pol_comb$Type <- factor(stats_pol_comb$Type, levels = c(
  "Main", "Female", "Male",
  "STEM", "Soc. Sciences", "Humanities",
  "High R-E", "High R-Not E", "Low R-E", "Low R-Not E",
  "1501+", "501-1500","101-500", "1-100",  
  "Non-US", "US"
))

# Color palette setup
color_values <- c(
  "Main" = "black",
  "Female" = "#E41A1C", "Male" = "#377EB8",
  "STEM" = "#4DAF4A", "Soc. Sciences" = "#FF7F00", "Humanities" = "#984EA3",
  "High R-E" = "#A65628", "High R-Not E" = "#F781BF",
  "Low R-E" = "#999999", "Low R-Not E" = "gold2",
  "1-100" = "#1F78B4", "101-500" = "#33A02C", "501-1500" = "#e31a1c", "1501+" = "#ff7f00",
  "US" = "red3", "Non-US" = "grey40"
)

# Also map 'Label' correctly to factor
stats_pol_comb$Label <- factor(stats_pol_comb$Label, levels = unique(stats_pol_comb$Label))
  
stats_pol_comb$Label <- factor(
  stats_pol_comb$Label,
  levels = c("Climate Action","Techno-Optimism", "Behavioural Adjustment")
)

# Calculate the 'Main' mean for each Label (facet column)
main_means <- stats_pol_comb %>%
  filter(Type == "Main") %>%
  group_by(Label) %>%
  summarize(Main_Mean = mean(Mean, na.rm = TRUE))

# Merge this back to the main dataset for plotting
stats_pol_comb <- stats_pol_comb %>%
  left_join(main_means, by = "Label")

p_all <- ggplot(stats_pol_comb %>% filter(Term %in% clim_var), aes(x = Mean, y = Type, color = Type, group = Type)) +
  geom_vline(data = main_means, aes(xintercept = Main_Mean), linetype = "dotted", color = "grey30", size = 0.5, alpha = 0.8) +  # Adjusted line thickness
  geom_vline(aes(xintercept = 0), linetype = "dotted", color = "grey99", size = 0.1, alpha = 0) +  # Adjusted line thickness
  geom_point(size = 2) +  # Reduced point size for journal compliance
  geom_errorbarh(aes(xmin = CI_lower, xmax = CI_upper), height = 0.2, size = 0.5) +  # Adjusted error bar thickness
  scale_color_manual(values = color_values) +
  labs(x = "Mean Value", y = "") +  # Removed title for a cleaner look
  theme_classic(base_size = 7) +  # Use journal-compliant font size
  theme(
    text = element_text(family = "Helvetica", size = 7),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    legend.position = "none",
    axis.text.y = element_text(size = 7, color = "grey30"),
    axis.text.x = element_text(size = 7, angle = 90, hjust = 1),
    strip.text = element_text(size = 7, face = "bold"),
    strip.background = element_blank(),
    strip.placement = "outside",
    panel.spacing.y = unit(0.5, "lines"),
    panel.spacing.x = unit(0.5, "lines")
  ) +
  facet_grid(rows = vars(Group), cols = vars(Label), scales = "free", space = "free_y", switch = "y")

# Save as EPS and PDF
ggsave("fig2.eps", p_all, device = cairo_ps, width = 180 / 25.4, height = 180 / 25.4)
ggsave("fig2.pdf", p_all, device = cairo_pdf, width = 180 / 25.4, height = 180 / 25.4)

```

Figure 3
```{r}
# Map the function over each variable group and combine results
stats_pol_main <- map_df(econ_var, ~calculate_stats(repl_df, .x))

stats_pol_is_female <- map_df(econ_var, ~calculate_stats(repl_df %>% filter(is_female==1), .x))
stats_pol_is_male <- map_df(econ_var, ~calculate_stats(repl_df %>% filter(is_male==1), .x))

stats_pol_is_stem <- map_df(econ_var, ~calculate_stats(repl_df %>% filter(is_stem==1), .x))
stats_pol_is_soc_sci <- map_df(econ_var, ~calculate_stats(repl_df %>% filter(is_soc_sci==1), .x))
stats_pol_is_humanities <- map_df(econ_var, ~calculate_stats(repl_df %>% filter(is_humanities==1), .x))

stats_pol_type_H_reach_H_exp_econ <- map_df(econ_var, ~calculate_stats(repl_df %>% filter(type_H_reach_H_exp_econ==1), .x))
stats_pol_type_H_reach_L_exp_econ <- map_df(econ_var, ~calculate_stats(repl_df %>% filter(type_H_reach_L_exp_econ==1), .x))
stats_pol_type_L_reach_H_exp_econ <- map_df(econ_var, ~calculate_stats(repl_df %>% filter(type_L_reach_H_exp_econ==1), .x))
stats_pol_type_L_reach_L_exp_econ <- map_df(econ_var, ~calculate_stats(repl_df %>% filter(type_L_reach_L_exp_econ==1), .x))

stats_pol_type_H_reach_H_exp_cult <- map_df(econ_var, ~calculate_stats(repl_df %>% filter(type_H_reach_H_exp_cult==1), .x))
stats_pol_type_H_reach_L_exp_cult <- map_df(econ_var, ~calculate_stats(repl_df %>% filter(type_H_reach_L_exp_cult==1), .x))
stats_pol_type_L_reach_H_exp_cult <- map_df(econ_var, ~calculate_stats(repl_df %>% filter(type_L_reach_H_exp_cult==1), .x))
stats_pol_type_L_reach_L_exp_cult <- map_df(econ_var, ~calculate_stats(repl_df %>% filter(type_L_reach_L_exp_cult==1), .x))

stats_pol_ranking_1_100 <- map_df(econ_var, ~calculate_stats(repl_df %>% filter(ranking_cat == "1-100"), .x))
stats_pol_ranking_1_100$Type <- "1-100"

stats_pol_ranking_101_500 <- map_df(econ_var, ~calculate_stats(repl_df %>% filter(ranking_cat == "101-500"), .x))
stats_pol_ranking_101_500$Type <- "101-500"

stats_pol_ranking_501_1500 <- map_df(econ_var, ~calculate_stats(repl_df %>% filter(ranking_cat == "501-1500"), .x))
stats_pol_ranking_501_1500$Type <- "501-1500"

stats_pol_ranking_1501 <- map_df(econ_var, ~calculate_stats(repl_df %>% filter(ranking_cat == "1501+"), .x))
stats_pol_ranking_1501$Type <- "1501+"

stats_pol_is_US <- map_df(econ_var, ~calculate_stats(repl_df %>% filter(is_US==1), .x))
stats_pol_isnt_US <- map_df(econ_var, ~calculate_stats(repl_df %>% filter(is_US==0), .x))

stats_pol_field <- bind_rows(
  mutate(stats_pol_is_humanities, Type = "Humanities"),
  mutate(stats_pol_is_soc_sci, Type = "Soc. Sciences"),
  mutate(stats_pol_is_stem, Type = "STEM")
)
stats_pol_field$Type <- factor(stats_pol_field$Type, levels = c("Humanities", "Soc. Sciences", "STEM"))

stats_pol_reach_by_exp_econ <- bind_rows(
  mutate(stats_pol_type_H_reach_H_exp_econ, Type = "High R-E"),
  mutate(stats_pol_type_H_reach_L_exp_econ, Type = "High R-Not E"),
  mutate(stats_pol_type_L_reach_H_exp_econ, Type = "Low R-E"),
  mutate(stats_pol_type_L_reach_L_exp_econ, Type = "Low R-Not E")
)
stats_pol_reach_by_exp_econ$Type <- factor(stats_pol_reach_by_exp_econ$Type, levels = c("High R-E", "High R-Not E", "Low R-E", "Low R-Not E"))

stats_pol_reach_by_exp_cult <- bind_rows(
  mutate(stats_pol_type_H_reach_H_exp_cult, Type = "High R-E"),
  mutate(stats_pol_type_H_reach_L_exp_cult, Type = "High R-Not E"),
  mutate(stats_pol_type_L_reach_H_exp_cult, Type = "Low R-E"),
  mutate(stats_pol_type_L_reach_L_exp_cult, Type = "Low R-Not E")
)
stats_pol_reach_by_exp_cult$Type <- factor(stats_pol_reach_by_exp_cult$Type, levels = c("High R-E", "High R-Not E", "Low R-E", "Low R-Not E"))

stats_pol_gender <- bind_rows(
  mutate(stats_pol_is_female, Type = "Female"),
  mutate(stats_pol_is_male, Type = "Male")
)
stats_pol_gender$Type <- factor(stats_pol_gender$Type, levels = c("Female", "Male"))

stats_pol_rank <- bind_rows(
  stats_pol_ranking_1_100,
  stats_pol_ranking_101_500,
  stats_pol_ranking_501_1500,
  stats_pol_ranking_1501
)
stats_pol_rank$Type <- factor(stats_pol_rank$Type, levels = c("1-100", "101-500", "501-1500", "1501+"))

stats_pol_US <- bind_rows(
  mutate(stats_pol_is_US, Type = "US"),
  mutate(stats_pol_isnt_US, Type = "Non-US")
)
stats_pol_US$Type <- factor(stats_pol_US$Type, levels = c("US", "Non-US"))

stats_pol_main$Type <- "Main"
stats_pol_main$Type <- factor(stats_pol_main$Type, levels = "Main")

stats_pol_main$Label <- factor(stats_pol_main$Term, levels = econ_var, labels = topic_label_mapping[econ_var])
stats_pol_field$Label <- factor(stats_pol_field$Term, levels = econ_var, labels = topic_label_mapping[econ_var])
stats_pol_reach_by_exp_econ$Label <- factor(stats_pol_reach_by_exp_econ$Term, levels = econ_var, labels = topic_label_mapping[econ_var])
stats_pol_reach_by_exp_cult$Label <- factor(stats_pol_reach_by_exp_cult$Term, levels = econ_var, labels = topic_label_mapping[econ_var])
stats_pol_gender$Label <- factor(stats_pol_gender$Term, levels = econ_var, labels = topic_label_mapping[econ_var])
stats_pol_rank$Label <- factor(stats_pol_rank$Term, levels = econ_var, labels = topic_label_mapping[econ_var])
stats_pol_US$Label <- factor(stats_pol_US$Term, levels = econ_var, labels = topic_label_mapping[econ_var])

stats_pol_comb <- bind_rows(stats_pol_main, stats_pol_field, 
                            stats_pol_reach_by_exp_econ %>%mutate(exp="econ"), 
                            stats_pol_reach_by_exp_cult%>%mutate(exp="cult"), 
                            stats_pol_gender, stats_pol_rank, stats_pol_US)

stats_pol_comb %<>% mutate(exp = ifelse(is.na(exp),"other", exp))
# Filter out the rows that don't meet the condition
stats_pol_comb %<>%
  filter(!(Label == "Cultural Liberalism" & exp == "econ")) %>%
  filter(!(Label == "Economic Collectivism" & exp == "cult"))
stats_pol_comb %<>% select(-exp)

stats_pol_comb$Group <- with(stats_pol_comb, case_when(
  Type %in% c("Main") ~ "Main",
  Type %in% c("Female", "Male") ~ "Gender",
  Type %in% c("STEM", "Soc. Sciences", "Humanities") ~ "Fields",
  Type %in% c("High R-E", "High R-Not E", "Low R-E", "Low R-Not E") ~ "Reach (R) by Expertise (E)",
  Type %in% c("1-100", "101-500", "501-1500", "1501+") ~ "University Rankings",
  Type %in% c("US", "Non-US") ~ "Country"
))
stats_pol_comb$Group <- factor(
  stats_pol_comb$Group,
  levels = c(
    "Main", 
    "Gender",
    "Fields",
    "Reach (R) by Expertise (E)",
    "University Rankings",
    "Country"
  )
)

# Ensure 'Type' has a proper order that reflects groupings
stats_pol_comb$Type <- factor(stats_pol_comb$Type, levels = c(
  "Main", "Female", "Male",
  "STEM", "Soc. Sciences", "Humanities",
  "High R-E", "High R-Not E", "Low R-E", "Low R-Not E",
  "1501+", "501-1500","101-500", "1-100",  
  "Non-US", "US"
))

# Color palette setup
color_values <- c(
  "Main" = "black",
  "Female" = "#E41A1C", "Male" = "#377EB8",
  "STEM" = "#4DAF4A", "Soc. Sciences" = "#FF7F00", "Humanities" = "#984EA3",
  "High R-E" = "#A65628", "High R-Not E" = "#F781BF",
  "Low R-E" = "#999999", "Low R-Not E" = "gold2",
  "1-100" = "#1F78B4", "101-500" = "#33A02C", "501-1500" = "#e31a1c", "1501+" = "#ff7f00",
  "US" = "red3", "Non-US" = "grey40"
)

# Also map 'Label' correctly to factor
stats_pol_comb$Label <- factor(stats_pol_comb$Label, levels = unique(stats_pol_comb$Label))
  
stats_pol_comb$Label <- factor(
  stats_pol_comb$Label,
  levels = c("Cultural Liberalism","Economic Collectivism")
)

# Calculate the 'Main' mean for each Label (facet column)
main_means <- stats_pol_comb %>%
  filter(Type == "Main") %>%
  group_by(Label) %>%
  summarize(Main_Mean = mean(Mean, na.rm = TRUE))

# Merge this back to the main dataset for plotting
stats_pol_comb <- stats_pol_comb %>%
  left_join(main_means, by = "Label")

# Adjusted Figure 3 plot
p_all_fig3 <- ggplot(stats_pol_comb %>% filter(Term %in% econ_var), aes(x = Mean, y = Type, color = Type, group = Type)) +
  geom_vline(data = main_means, aes(xintercept = Main_Mean), linetype = "dotted", color = "grey60", size = 0.5) +
  geom_vline(aes(xintercept = 0), linetype = "dotted", color = "grey99", size = 0.1, alpha = 0) +  # Adjusted line thickness
  geom_point(size = 2) +
  geom_errorbarh(aes(xmin = CI_lower, xmax = CI_upper), height = 0.2, size = 0.5) +
  scale_color_manual(values = color_values) +
  labs(x = "Mean Value", y = NULL) +
  theme_classic(base_size = 7) +
  theme(
    text = element_text(family = "Helvetica"),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    strip.text = element_text(face = "bold", size = 7),
    axis.text.x = element_text(size = 7, angle = 45, hjust = 1),
    axis.text.y = element_text(size = 7),
    legend.position = "none",
    strip.background = element_blank(),
    strip.placement = "outside",
    panel.spacing = unit(0.5, "lines")
  ) +
  facet_grid(rows = vars(Group), cols = vars(Label), scales = "free", space = "free_y", switch = "y")

# Save as EPS and PDF
ggsave("fig3.eps", p_all_fig3, width = 180 / 25.4, height = 180 / 25.4, device = cairo_ps)
ggsave("fig3.pdf", p_all_fig3, width = 180 / 25.4, height = 180 / 25.4, device = cairo_pdf)


```


Figure 4
```{r}
# Map the function over each variable group and combine results
stats_pol_main <- map_df(beh_var, ~calculate_stats(repl_df, .x))

stats_pol_is_female <- map_df(beh_var, ~calculate_stats(repl_df %>% filter(is_female==1), .x))
stats_pol_is_male <- map_df(beh_var, ~calculate_stats(repl_df %>% filter(is_male==1), .x))

stats_pol_is_stem <- map_df(beh_var, ~calculate_stats(repl_df %>% filter(is_stem==1), .x))
stats_pol_is_soc_sci <- map_df(beh_var, ~calculate_stats(repl_df %>% filter(is_soc_sci==1), .x))
stats_pol_is_humanities <- map_df(beh_var, ~calculate_stats(repl_df %>% filter(is_humanities==1), .x))

stats_pol_type_H_reach_H_cred <- map_df(beh_var, ~calculate_stats(repl_df %>% filter(type_H_reach_H_cred==1), .x))
stats_pol_type_H_reach_L_cred <- map_df(beh_var, ~calculate_stats(repl_df %>% filter(type_H_reach_L_cred==1), .x))
stats_pol_type_L_reach_H_cred <- map_df(beh_var, ~calculate_stats(repl_df %>% filter(type_L_reach_H_cred==1), .x))
stats_pol_type_L_reach_L_cred <- map_df(beh_var, ~calculate_stats(repl_df %>% filter(type_L_reach_L_cred==1), .x))

stats_pol_ranking_1_100 <- map_df(beh_var, ~calculate_stats(repl_df %>% filter(ranking_cat == "1-100"), .x))
stats_pol_ranking_1_100$Type <- "1-100"

stats_pol_ranking_101_500 <- map_df(beh_var, ~calculate_stats(repl_df %>% filter(ranking_cat == "101-500"), .x))
stats_pol_ranking_101_500$Type <- "101-500"

stats_pol_ranking_501_1500 <- map_df(beh_var, ~calculate_stats(repl_df %>% filter(ranking_cat == "501-1500"), .x))
stats_pol_ranking_501_1500$Type <- "501-1500"

stats_pol_ranking_1501 <- map_df(beh_var, ~calculate_stats(repl_df %>% filter(ranking_cat == "1501+"), .x))
stats_pol_ranking_1501$Type <- "1501+"

stats_pol_is_US <- map_df(beh_var, ~calculate_stats(repl_df %>% filter(is_US==1), .x))
stats_pol_isnt_US <- map_df(beh_var, ~calculate_stats(repl_df %>% filter(is_US==0), .x))

stats_pol_field <- bind_rows(
  mutate(stats_pol_is_humanities, Type = "Humanities"),
  mutate(stats_pol_is_soc_sci, Type = "Soc. Sciences"),
  mutate(stats_pol_is_stem, Type = "STEM")
)
stats_pol_field$Type <- factor(stats_pol_field$Type, levels = c("Humanities", "Soc. Sciences", "STEM"))

stats_pol_reach_by_cred <- bind_rows(
  mutate(stats_pol_type_H_reach_H_cred, Type = "High R-High C"),
  mutate(stats_pol_type_H_reach_L_cred, Type = "High R-Low C"),
  mutate(stats_pol_type_L_reach_H_cred, Type = "Low R-High C"),
  mutate(stats_pol_type_L_reach_L_cred, Type = "Low R-Low C")
)
stats_pol_reach_by_cred$Type <- factor(stats_pol_reach_by_cred$Type, levels = c("High R-High C", "High R-Low C", "Low R-High C", "Low R-Low C"))

stats_pol_gender <- bind_rows(
  mutate(stats_pol_is_female, Type = "Female"),
  mutate(stats_pol_is_male, Type = "Male")
)
stats_pol_gender$Type <- factor(stats_pol_gender$Type, levels = c("Female", "Male"))

stats_pol_rank <- bind_rows(
  stats_pol_ranking_1_100,
  stats_pol_ranking_101_500,
  stats_pol_ranking_501_1500,
  stats_pol_ranking_1501
)
stats_pol_rank$Type <- factor(stats_pol_rank$Type, levels = c("1-100", "101-500", "501-1500", "1501+"))

stats_pol_US <- bind_rows(
  mutate(stats_pol_is_US, Type = "US"),
  mutate(stats_pol_isnt_US, Type = "Non-US")
)
stats_pol_US$Type <- factor(stats_pol_US$Type, levels = c("US", "Non-US"))

stats_pol_main$Type <- "Main"
stats_pol_main$Type <- factor(stats_pol_main$Type, levels = "Main")

stats_pol_main$Label <- factor(stats_pol_main$Term, levels = beh_var, labels = topic_label_mapping[beh_var])
stats_pol_field$Label <- factor(stats_pol_field$Term, levels = beh_var, labels = topic_label_mapping[beh_var])
stats_pol_reach_by_cred$Label <- factor(stats_pol_reach_by_cred$Term, levels = beh_var, labels = topic_label_mapping[beh_var])
stats_pol_gender$Label <- factor(stats_pol_gender$Term, levels = beh_var, labels = topic_label_mapping[beh_var])
stats_pol_rank$Label <- factor(stats_pol_rank$Term, levels = beh_var, labels = topic_label_mapping[beh_var])
stats_pol_US$Label <- factor(stats_pol_US$Term, levels = beh_var, labels = topic_label_mapping[beh_var])

stats_pol_comb <- bind_rows(stats_pol_main, stats_pol_field, stats_pol_reach_by_cred, stats_pol_gender, stats_pol_rank, stats_pol_US)

stats_pol_comb$Group <- with(stats_pol_comb, case_when(
  Type %in% c("Main") ~ "Main",
  Type %in% c("Female", "Male") ~ "Gender",
  Type %in% c("STEM", "Soc. Sciences", "Humanities") ~ "Fields",
  Type %in% c("High R-High C", "High R-Low C", "Low R-High C", "Low R-Low C") ~ "Reach (R) by Credibility (C)",
  Type %in% c("1-100", "101-500", "501-1500", "1501+") ~ "University Rankings",
  Type %in% c("US", "Non-US") ~ "Country"
))
stats_pol_comb$Group <- factor(
  stats_pol_comb$Group,
  levels = c(
    "Main", 
    "Gender",
    "Fields",
    "Reach (R) by Credibility (C)",
    "University Rankings",
    "Country"
  )
)

# Ensure 'Type' has a proper order that reflects groupings
stats_pol_comb$Type <- factor(stats_pol_comb$Type, levels = c(
  "Main", "Female", "Male",
  "STEM", "Soc. Sciences", "Humanities",
  "High R-High C", "High R-Low C", "Low R-High C", "Low R-Low C",
  "1501+", "501-1500","101-500", "1-100",  
  "Non-US", "US"
))

# Color palette setup
color_values <- c(
  "Main" = "black",
  "Female" = "#E41A1C", "Male" = "#377EB8",
  "STEM" = "#4DAF4A", "Soc. Sciences" = "#FF7F00", "Humanities" = "#984EA3",
  "High R-High C" = "#A65628", "High R-Low C" = "#F781BF",
  "Low R-High C" = "#999999", "Low R-Low C" = "gold2",
  "1-100" = "#1F78B4", "101-500" = "#33A02C", "501-1500" = "#e31a1c", "1501+" = "#ff7f00",
  "US" = "red3", "Non-US" = "grey40"
)

# Also map 'Label' correctly to factor
stats_pol_comb$Label <- factor(stats_pol_comb$Label, levels = unique(stats_pol_comb$Label))
  
stats_pol_comb$Label <- factor(
  stats_pol_comb$Label,
  levels = c("Egocentrism","Toxicity", "Emotionality/Reasoning")
)

# Calculate the 'Main' mean for each Label (facet column)
main_means <- stats_pol_comb %>%
  filter(Type == "Main") %>%
  group_by(Label) %>%
  summarize(Main_Mean = mean(Mean, na.rm = TRUE))

# Merge this back to the main dataset for plotting
stats_pol_comb <- stats_pol_comb %>%
  left_join(main_means, by = "Label")

# Adjusted Figure 4 plot
p_all_fig4 <- ggplot(stats_pol_comb %>% filter(Term %in% beh_var), aes(x = Mean, y = Type, color = Type, group = Type)) +
  # Conditional vertical lines based on Label
  geom_vline(data = stats_pol_comb %>% distinct(Label) %>% 
               mutate(xintercept = ifelse(Label == "Emotionality/Reasoning", 1, 0)),
             aes(xintercept = xintercept), linetype = "dotted", color = "grey99", size = 0.1, alpha = 0) +
  geom_vline(data = main_means, aes(xintercept = Main_Mean), linetype = "dotted", color = "grey60", size = 0.5) +
  geom_point(size = 2) +
  geom_errorbarh(aes(xmin = CI_lower, xmax = CI_upper), height = 0.2, size = 0.5) +
  scale_color_manual(values = color_values) +
  labs(x = "Mean Value", y = NULL) +
  theme_classic(base_size = 7) +
  theme(
    text = element_text(family = "Helvetica"),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    strip.text = element_text(face = "bold", size = 7),
    axis.text.x = element_text(size = 7, angle = 45, hjust = 1),
    axis.text.y = element_text(size = 7),
    legend.position = "none",
    strip.background = element_blank(),
    strip.placement = "outside",
    panel.spacing = unit(0.5, "lines")
  ) +
  facet_grid(rows = vars(Group), cols = vars(Label), scales = "free", space = "free_y", switch = "y")

# Save as EPS and PDF
ggsave("fig4.eps", p_all_fig4, width = 180 / 25.4, height = 180 / 25.4, device = cairo_ps)
ggsave("fig4.pdf", p_all_fig4, width = 180 / 25.4, height = 180 / 25.4, device = cairo_pdf)

```


# Extended Data Figures



Extended Data Figure 2
```{r}
# Map the function over each variable group and combine results
stats_pol_main <- map_df(clim_var, ~calculate_stats(repl_df, .x))

stats_pol_is_female <- map_df(clim_var, ~calculate_stats(repl_df %>% filter(is_female==1), .x))
stats_pol_is_male <- map_df(clim_var, ~calculate_stats(repl_df %>% filter(is_male==1), .x))

stats_pol_is_stem <- map_df(clim_var, ~calculate_stats(repl_df %>% filter(is_stem==1), .x))
stats_pol_is_soc_sci <- map_df(clim_var, ~calculate_stats(repl_df %>% filter(is_soc_sci==1), .x))
stats_pol_is_humanities <- map_df(clim_var, ~calculate_stats(repl_df %>% filter(is_humanities==1), .x))

stats_pol_type_H_reach_H_exp_climate <- map_df(clim_var, ~calculate_stats(repl_df %>% filter(type_H_reach_H_exp_climate==1), .x))
stats_pol_type_H_reach_L_exp_climate <- map_df(clim_var, ~calculate_stats(repl_df %>% filter(type_H_reach_L_exp_climate==1), .x))
stats_pol_type_L_reach_H_exp_climate <- map_df(clim_var, ~calculate_stats(repl_df %>% filter(type_L_reach_H_exp_climate==1), .x))
stats_pol_type_L_reach_L_exp_climate <- map_df(clim_var, ~calculate_stats(repl_df %>% filter(type_L_reach_L_exp_climate==1), .x))

stats_pol_ranking_1_100 <- map_df(clim_var, ~calculate_stats(repl_df %>% filter(ranking_cat == "1-100"), .x))
stats_pol_ranking_1_100$Type <- "1-100"

stats_pol_ranking_101_500 <- map_df(clim_var, ~calculate_stats(repl_df %>% filter(ranking_cat == "101-500"), .x))
stats_pol_ranking_101_500$Type <- "101-500"

stats_pol_ranking_501_1500 <- map_df(clim_var, ~calculate_stats(repl_df %>% filter(ranking_cat == "501-1500"), .x))
stats_pol_ranking_501_1500$Type <- "501-1500"

stats_pol_ranking_1501 <- map_df(clim_var, ~calculate_stats(repl_df %>% filter(ranking_cat == "1501+"), .x))
stats_pol_ranking_1501$Type <- "1501+"

stats_pol_is_US <- map_df(clim_var, ~calculate_stats(repl_df %>% filter(is_US==1), .x))
stats_pol_isnt_US <- map_df(clim_var, ~calculate_stats(repl_df %>% filter(is_US==0), .x))

stats_pol_us_users <- map_df(clim_var, ~calculate_stats(users_df %>% filter(is_bot_50==0), .x))

stats_pol_field <- bind_rows(
  mutate(stats_pol_is_humanities, Type = "Humanities"),
  mutate(stats_pol_is_soc_sci, Type = "Soc. Sciences"),
  mutate(stats_pol_is_stem, Type = "STEM")
)
stats_pol_field$Type <- factor(stats_pol_field$Type, levels = c("Humanities", "Soc. Sciences", "STEM"))

stats_pol_reach_by_exp_climate <- bind_rows(
  mutate(stats_pol_type_H_reach_H_exp_climate, Type = "High R-E"),
  mutate(stats_pol_type_H_reach_L_exp_climate, Type = "High R-Not E"),
  mutate(stats_pol_type_L_reach_H_exp_climate, Type = "Low R-E"),
  mutate(stats_pol_type_L_reach_L_exp_climate, Type = "Low R-Not E")
)
stats_pol_reach_by_exp_climate$Type <- factor(stats_pol_reach_by_exp_climate$Type, levels = c("High R-E", "High R-Not E", "Low R-E", "Low R-Not E"))

stats_pol_gender <- bind_rows(
  mutate(stats_pol_is_female, Type = "Female"),
  mutate(stats_pol_is_male, Type = "Male")
)
stats_pol_gender$Type <- factor(stats_pol_gender$Type, levels = c("Female", "Male"))

stats_pol_rank <- bind_rows(
  stats_pol_ranking_1_100,
  stats_pol_ranking_101_500,
  stats_pol_ranking_501_1500,
  stats_pol_ranking_1501
)
stats_pol_rank$Type <- factor(stats_pol_rank$Type, levels = c("1-100", "101-500", "501-1500", "1501+"))

stats_pol_US <- bind_rows(
  mutate(stats_pol_is_US, Type = "US"),
  mutate(stats_pol_isnt_US, Type = "Non-US")
)
stats_pol_US$Type <- factor(stats_pol_US$Type, levels = c("US", "Non-US"))

stats_pol_main$Type <- "Main"
stats_pol_main$Type <- factor(stats_pol_main$Type, levels = "Main")

stats_pol_us_users$Type <- "US users"
stats_pol_us_users$Type <- factor(stats_pol_us_users$Type, levels = "US users")

stats_pol_main$Label <- factor(stats_pol_main$Term, levels = clim_var, labels = topic_label_mapping[clim_var])
stats_pol_field$Label <- factor(stats_pol_field$Term, levels = clim_var, labels = topic_label_mapping[clim_var])
stats_pol_reach_by_exp_climate$Label <- factor(stats_pol_reach_by_exp_climate$Term, levels = clim_var, labels = topic_label_mapping[clim_var])
stats_pol_gender$Label <- factor(stats_pol_gender$Term, levels = clim_var, labels = topic_label_mapping[clim_var])
stats_pol_rank$Label <- factor(stats_pol_rank$Term, levels = clim_var, labels = topic_label_mapping[clim_var])
stats_pol_US$Label <- factor(stats_pol_US$Term, levels = clim_var, labels = topic_label_mapping[clim_var])
stats_pol_us_users$Label <- factor(stats_pol_us_users$Term, levels = clim_var, labels = topic_label_mapping[clim_var])

stats_pol_comb <- bind_rows(stats_pol_main, stats_pol_field, stats_pol_reach_by_exp_climate, stats_pol_gender, stats_pol_rank, stats_pol_US, stats_pol_us_users)

# Extract the US users values for each Term
us_users_values <- stats_pol_comb %>%
  filter(Type == "US users") %>%
  select(Term, Mean, StdError, CI_lower, CI_upper) %>%
  rename(US_users_Mean = Mean, US_users_StdError = StdError, US_users_CI_lower = CI_lower, US_users_CI_upper = CI_upper)

# Join the US users values with the original dataframe
stats_pol_comb <- stats_pol_comb %>%
  left_join(us_users_values, by = "Term") %>%
  mutate(
    Mean = Mean / US_users_Mean,
    StdError = StdError / US_users_StdError,
    CI_lower = CI_lower / US_users_CI_lower,
    CI_upper = CI_upper / US_users_CI_upper
  ) %>%
  select(Term, Type, Label, Mean, StdError, CI_lower, CI_upper)

stats_pol_comb %<>% filter(Type!="US users")

# stats_pol_climate
stats_pol_comb$Group <- with(stats_pol_comb, case_when(
  Type %in% c("Main") ~ "Main",
  Type %in% c("Female", "Male") ~ "Gender",
  Type %in% c("STEM", "Soc. Sciences", "Humanities") ~ "Fields",
  Type %in% c("High R-E", "High R-Not E", "Low R-E", "Low R-Not E") ~ "Reach (R) by Expertise (E)",
  Type %in% c("1-100", "101-500", "501-1500", "1501+") ~ "University Rankings",
  Type %in% c("US", "Non-US") ~ "Country",
  Type %in% c("US users") ~ "US General Twitter Users"
))
stats_pol_comb$Group <- factor(
  stats_pol_comb$Group,
  levels = c(
    "Main", 
    "Gender",
    "Fields",
    "Reach (R) by Expertise (E)",
    "University Rankings",
    "Country",
    "US General Twitter Users"
  )
)

# Ensure 'Type' has a proper order that reflects groupings
stats_pol_comb$Type <- factor(stats_pol_comb$Type, levels = c(
  "Main", "Female", "Male",
  "STEM", "Soc. Sciences", "Humanities",
  "High R-E", "High R-Not E", "Low R-E", "Low R-Not E",
  "1501+", "501-1500","101-500", "1-100",  
  "Non-US", "US",
  "US users"
))

# Color palette setup
color_values <- c(
  "Main" = "black",
  "Female" = "#E41A1C", "Male" = "#377EB8",
  "STEM" = "#4DAF4A", "Soc. Sciences" = "#FF7F00", "Humanities" = "#984EA3",
  "High R-E" = "#A65628", "High R-Not E" = "#F781BF",
  "Low R-E" = "#999999", "Low R-Not E" = "gold2",
  "1-100" = "#1F78B4", "101-500" = "#33A02C", "501-1500" = "#e31a1c", "1501+" = "#ff7f00",
  "US" = "red3", "Non-US" = "grey40",
  "US users" = "purple3"
)

# Also map 'Label' correctly to factor
stats_pol_comb$Label <- factor(stats_pol_comb$Label, levels = unique(stats_pol_comb$Label))
  
stats_pol_comb$Label <- factor(
  stats_pol_comb$Label,
  levels = c("Climate Action","Techno-Optimism", "Behavioural Adjustment")
)

# Calculate the 'Main' mean for each Label (facet column)
main_means <- stats_pol_comb %>%
  filter(Type == "Main") %>%
  group_by(Label) %>%
  summarize(Main_Mean = mean(Mean, na.rm = TRUE))

# Merge this back to the main dataset for plotting
stats_pol_comb <- stats_pol_comb %>%
  left_join(main_means, by = "Label")

p_all <- ggplot(stats_pol_comb %>% filter(Term %in% clim_var), aes(x = Mean, y = Type, color = Type, group = Type)) +
  geom_vline(data = main_means, aes(xintercept = Main_Mean), linetype = "dotted", color = "grey30", size = 0.5, alpha = 0.8) +  # Adjusted line thickness
  geom_vline(aes(xintercept = 0), linetype = "dotted", color = "grey99", size = 0.1, alpha = 0) +  # Adjusted line thickness
  geom_point(size = 2) +  # Reduced point size for journal compliance
  geom_errorbarh(aes(xmin = CI_lower, xmax = CI_upper), height = 0.2, size = 0.5) +  # Adjusted error bar thickness
  scale_color_manual(values = color_values) +
  labs(x = "Mean Value", y = "") +  # Removed title for a cleaner look
  theme_classic(base_size = 7) +  # Use journal-compliant font size
  theme(
    text = element_text(family = "Helvetica", size = 7),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    legend.position = "none",
    axis.text.y = element_text(size = 7, color = "grey30"),
    axis.text.x = element_text(size = 7, angle = 90, hjust = 1),
    strip.text = element_text(size = 7, face = "bold"),
    strip.background = element_blank(),
    strip.placement = "outside",
    panel.spacing.y = unit(0.5, "lines"),
    panel.spacing.x = unit(0.5, "lines")
  ) +
  facet_grid(rows = vars(Group), cols = vars(Label), scales = "free", space = "free_y", switch = "y")

# Save as EPS and PDF
ggsave("edf2.eps", p_all, device = cairo_ps, width = 180 / 25.4, height = 180 / 25.4)
ggsave("edf2.pdf", p_all, device = cairo_pdf, width = 180 / 25.4, height = 180 / 25.4)

```
 
Extended Data Figure 3
```{r}
# Map the function over each variable group and combine results
stats_pol_main <- map_df(econ_var, ~calculate_stats(repl_df, .x))

stats_pol_is_female <- map_df(econ_var, ~calculate_stats(repl_df %>% filter(is_female==1), .x))
stats_pol_is_male <- map_df(econ_var, ~calculate_stats(repl_df %>% filter(is_male==1), .x))

stats_pol_is_stem <- map_df(econ_var, ~calculate_stats(repl_df %>% filter(is_stem==1), .x))
stats_pol_is_soc_sci <- map_df(econ_var, ~calculate_stats(repl_df %>% filter(is_soc_sci==1), .x))
stats_pol_is_humanities <- map_df(econ_var, ~calculate_stats(repl_df %>% filter(is_humanities==1), .x))

stats_pol_type_H_reach_H_exp_econ <- map_df(econ_var, ~calculate_stats(repl_df %>% filter(type_H_reach_H_exp_econ==1), .x))
stats_pol_type_H_reach_L_exp_econ <- map_df(econ_var, ~calculate_stats(repl_df %>% filter(type_H_reach_L_exp_econ==1), .x))
stats_pol_type_L_reach_H_exp_econ <- map_df(econ_var, ~calculate_stats(repl_df %>% filter(type_L_reach_H_exp_econ==1), .x))
stats_pol_type_L_reach_L_exp_econ <- map_df(econ_var, ~calculate_stats(repl_df %>% filter(type_L_reach_L_exp_econ==1), .x))

stats_pol_type_H_reach_H_exp_cult <- map_df(econ_var, ~calculate_stats(repl_df %>% filter(type_H_reach_H_exp_cult==1), .x))
stats_pol_type_H_reach_L_exp_cult <- map_df(econ_var, ~calculate_stats(repl_df %>% filter(type_H_reach_L_exp_cult==1), .x))
stats_pol_type_L_reach_H_exp_cult <- map_df(econ_var, ~calculate_stats(repl_df %>% filter(type_L_reach_H_exp_cult==1), .x))
stats_pol_type_L_reach_L_exp_cult <- map_df(econ_var, ~calculate_stats(repl_df %>% filter(type_L_reach_L_exp_cult==1), .x))

stats_pol_ranking_1_100 <- map_df(econ_var, ~calculate_stats(repl_df %>% filter(ranking_cat == "1-100"), .x))
stats_pol_ranking_1_100$Type <- "1-100"

stats_pol_ranking_101_500 <- map_df(econ_var, ~calculate_stats(repl_df %>% filter(ranking_cat == "101-500"), .x))
stats_pol_ranking_101_500$Type <- "101-500"

stats_pol_ranking_501_1500 <- map_df(econ_var, ~calculate_stats(repl_df %>% filter(ranking_cat == "501-1500"), .x))
stats_pol_ranking_501_1500$Type <- "501-1500"

stats_pol_ranking_1501 <- map_df(econ_var, ~calculate_stats(repl_df %>% filter(ranking_cat == "1501+"), .x))
stats_pol_ranking_1501$Type <- "1501+"

stats_pol_is_US <- map_df(econ_var, ~calculate_stats(repl_df %>% filter(is_US==1), .x))
stats_pol_isnt_US <- map_df(econ_var, ~calculate_stats(repl_df %>% filter(is_US==0), .x))

stats_pol_us_users <- map_df(econ_var, ~calculate_stats(users_df%>% filter(is_bot_50==0), .x))

stats_pol_field <- bind_rows(
  mutate(stats_pol_is_humanities, Type = "Humanities"),
  mutate(stats_pol_is_soc_sci, Type = "Soc. Sciences"),
  mutate(stats_pol_is_stem, Type = "STEM")
)
stats_pol_field$Type <- factor(stats_pol_field$Type, levels = c("Humanities", "Soc. Sciences", "STEM"))

stats_pol_reach_by_exp_econ <- bind_rows(
  mutate(stats_pol_type_H_reach_H_exp_econ, Type = "High R-E"),
  mutate(stats_pol_type_H_reach_L_exp_econ, Type = "High R-Not E"),
  mutate(stats_pol_type_L_reach_H_exp_econ, Type = "Low R-E"),
  mutate(stats_pol_type_L_reach_L_exp_econ, Type = "Low R-Not E")
)
stats_pol_reach_by_exp_econ$Type <- factor(stats_pol_reach_by_exp_econ$Type, levels = c("High R-E", "High R-Not E", "Low R-E", "Low R-Not E"))

stats_pol_reach_by_exp_cult <- bind_rows(
  mutate(stats_pol_type_H_reach_H_exp_cult, Type = "High R-E"),
  mutate(stats_pol_type_H_reach_L_exp_cult, Type = "High R-Not E"),
  mutate(stats_pol_type_L_reach_H_exp_cult, Type = "Low R-E"),
  mutate(stats_pol_type_L_reach_L_exp_cult, Type = "Low R-Not E")
)
stats_pol_reach_by_exp_cult$Type <- factor(stats_pol_reach_by_exp_cult$Type, levels = c("High R-E", "High R-Not E", "Low R-E", "Low R-Not E"))

stats_pol_gender <- bind_rows(
  mutate(stats_pol_is_female, Type = "Female"),
  mutate(stats_pol_is_male, Type = "Male")
)
stats_pol_gender$Type <- factor(stats_pol_gender$Type, levels = c("Female", "Male"))

stats_pol_rank <- bind_rows(
  stats_pol_ranking_1_100,
  stats_pol_ranking_101_500,
  stats_pol_ranking_501_1500,
  stats_pol_ranking_1501
)
stats_pol_rank$Type <- factor(stats_pol_rank$Type, levels = c("1-100", "101-500", "501-1500", "1501+"))

stats_pol_US <- bind_rows(
  mutate(stats_pol_is_US, Type = "US"),
  mutate(stats_pol_isnt_US, Type = "Non-US")
)
stats_pol_US$Type <- factor(stats_pol_US$Type, levels = c("US", "Non-US"))

stats_pol_main$Type <- "Main"
stats_pol_main$Type <- factor(stats_pol_main$Type, levels = "Main")

stats_pol_us_users$Type <- "US users"
stats_pol_us_users$Type <- factor(stats_pol_us_users$Type, levels = "US users")

stats_pol_main$Label <- factor(stats_pol_main$Term, levels = econ_var, labels = topic_label_mapping[econ_var])
stats_pol_field$Label <- factor(stats_pol_field$Term, levels = econ_var, labels = topic_label_mapping[econ_var])
stats_pol_reach_by_exp_econ$Label <- factor(stats_pol_reach_by_exp_econ$Term, levels = econ_var, labels = topic_label_mapping[econ_var])
stats_pol_reach_by_exp_cult$Label <- factor(stats_pol_reach_by_exp_cult$Term, levels = econ_var, labels = topic_label_mapping[econ_var])
stats_pol_gender$Label <- factor(stats_pol_gender$Term, levels = econ_var, labels = topic_label_mapping[econ_var])
stats_pol_rank$Label <- factor(stats_pol_rank$Term, levels = econ_var, labels = topic_label_mapping[econ_var])
stats_pol_US$Label <- factor(stats_pol_US$Term, levels = econ_var, labels = topic_label_mapping[econ_var])
stats_pol_us_users$Label <- factor(stats_pol_us_users$Term, levels = econ_var, labels = topic_label_mapping[econ_var])

stats_pol_comb <- bind_rows(stats_pol_main, stats_pol_field, 
                            stats_pol_reach_by_exp_econ %>%mutate(exp="econ"), 
                            stats_pol_reach_by_exp_cult%>%mutate(exp="cult"), 
                            stats_pol_gender, stats_pol_rank, stats_pol_US,stats_pol_us_users)

stats_pol_comb %<>% mutate(exp = ifelse(is.na(exp),"other", exp))
# Filter out the rows that don't meet the condition
stats_pol_comb %<>%
  filter(!(Label == "Cultural Liberalism" & exp == "econ")) %>%
  filter(!(Label == "Economic Collectivism" & exp == "cult"))
stats_pol_comb %<>% select(-exp)

# Extract the US users values for each Term
us_users_values <- stats_pol_comb %>%
  filter(Type == "US users") %>%
  select(Term, Mean, StdError, CI_lower, CI_upper) %>%
  rename(US_users_Mean = Mean, US_users_StdError = StdError, US_users_CI_lower = CI_lower, US_users_CI_upper = CI_upper)

# Join the US users values with the original dataframe
stats_pol_comb <- stats_pol_comb %>%
  left_join(us_users_values, by = "Term") %>%
  mutate(
    Mean = Mean / US_users_Mean,
    StdError = StdError / US_users_StdError,
    CI_lower = CI_lower / US_users_CI_lower,
    CI_upper = CI_upper / US_users_CI_upper
  ) %>%
  select(Term, Type, Label, Mean, StdError, CI_lower, CI_upper)

stats_pol_comb %<>% filter(Type!="US users")

stats_pol_comb$Group <- with(stats_pol_comb, case_when(
  Type %in% c("Main") ~ "Main",
  Type %in% c("Female", "Male") ~ "Gender",
  Type %in% c("STEM", "Soc. Sciences", "Humanities") ~ "Fields",
  Type %in% c("High R-E", "High R-Not E", "Low R-E", "Low R-Not E") ~ "Reach (R) by Expertise (E)",
  Type %in% c("1-100", "101-500", "501-1500", "1501+") ~ "University Rankings",
  Type %in% c("US", "Non-US") ~ "Country",
  Type %in% c("US users") ~ "US General Twitter Users"
))
stats_pol_comb$Group <- factor(
  stats_pol_comb$Group,
  levels = c(
    "Main", 
    "Gender",
    "Fields",
    "Reach (R) by Expertise (E)",
    "University Rankings",
    "Country",
    "Field Match",
    "US General Twitter Users"
  )
)

# Ensure 'Type' has a proper order that reflects groupings
stats_pol_comb$Type <- factor(stats_pol_comb$Type, levels = c(
  "Main", "Female", "Male",
  "STEM", "Soc. Sciences", "Humanities",
  "High R-E", "High R-Not E", "Low R-E", "Low R-Not E",
  "1501+", "501-1500","101-500", "1-100",  
  "Non-US", "US",
  "Does Culture", "Does Economics", "Does Neither",
  "US users"
))

# Color palette setup
color_values <- c(
  "Main" = "black",
  "Female" = "#E41A1C", "Male" = "#377EB8",
  "STEM" = "#4DAF4A", "Soc. Sciences" = "#FF7F00", "Humanities" = "#984EA3",
  "High R-E" = "#A65628", "High R-Not E" = "#F781BF",
  "Low R-E" = "#999999", "Low R-Not E" = "gold2",
  "1-100" = "#1F78B4", "101-500" = "#33A02C", "501-1500" = "#e31a1c", "1501+" = "#ff7f00",
  "US" = "red3", "Non-US" = "grey40",
  "Does Culture" = "cyan3", "Does Economics" = "orange2", "Does Neither" = "grey40",
  "US users"="purple3"
)

# Also map 'Label' correctly to factor
stats_pol_comb$Label <- factor(stats_pol_comb$Label, levels = unique(stats_pol_comb$Label))
  
stats_pol_comb$Label <- factor(
  stats_pol_comb$Label,
  levels = c("Cultural Liberalism","Economic Collectivism")
)

# Calculate the 'Main' mean for each Label (facet column)
main_means <- stats_pol_comb %>%
  filter(Type == "Main") %>%
  group_by(Label) %>%
  summarize(Main_Mean = mean(Mean, na.rm = TRUE))

# Merge this back to the main dataset for plotting
stats_pol_comb <- stats_pol_comb %>%
  left_join(main_means, by = "Label")


# Adjusted Figure 3 plot
p_all_fig3 <- ggplot(stats_pol_comb %>% filter(Term %in% econ_var), aes(x = Mean, y = Type, color = Type, group = Type)) +
  geom_vline(data = main_means, aes(xintercept = Main_Mean), linetype = "dotted", color = "grey60", size = 0.5) +
  geom_vline(aes(xintercept = 0), linetype = "dotted", color = "grey99", size = 0.1, alpha = 0) +  # Adjusted line thickness
  geom_point(size = 2) +
  geom_errorbarh(aes(xmin = CI_lower, xmax = CI_upper), height = 0.2, size = 0.5) +
  scale_color_manual(values = color_values) +
  labs(x = "Mean Value", y = NULL) +
  theme_classic(base_size = 7) +
  theme(
    text = element_text(family = "Helvetica"),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    strip.text = element_text(face = "bold", size = 7),
    axis.text.x = element_text(size = 7, angle = 45, hjust = 1),
    axis.text.y = element_text(size = 7),
    legend.position = "none",
    strip.background = element_blank(),
    strip.placement = "outside",
    panel.spacing = unit(0.5, "lines")
  ) +
  facet_grid(rows = vars(Group), cols = vars(Label), scales = "free", space = "free_y", switch = "y")

# Save as EPS and PDF
ggsave("edf3.eps", p_all_fig3, width = 180 / 25.4, height = 180 / 25.4, device = cairo_ps)
ggsave("edf3.pdf", p_all_fig3, width = 180 / 25.4, height = 180 / 25.4, device = cairo_pdf)

```
 

Extended Data Figure 4
```{r}
# Map the function over each variable group and combine results
stats_pol_main <- map_df(beh_var, ~calculate_stats(repl_df, .x))

stats_pol_is_female <- map_df(beh_var, ~calculate_stats(repl_df %>% filter(is_female==1), .x))
stats_pol_is_male <- map_df(beh_var, ~calculate_stats(repl_df %>% filter(is_male==1), .x))

stats_pol_is_stem <- map_df(beh_var, ~calculate_stats(repl_df %>% filter(is_stem==1), .x))
stats_pol_is_soc_sci <- map_df(beh_var, ~calculate_stats(repl_df %>% filter(is_soc_sci==1), .x))
stats_pol_is_humanities <- map_df(beh_var, ~calculate_stats(repl_df %>% filter(is_humanities==1), .x))

stats_pol_type_H_reach_H_cred <- map_df(beh_var, ~calculate_stats(repl_df %>% filter(type_H_reach_H_cred==1), .x))
stats_pol_type_H_reach_L_cred <- map_df(beh_var, ~calculate_stats(repl_df %>% filter(type_H_reach_L_cred==1), .x))
stats_pol_type_L_reach_H_cred <- map_df(beh_var, ~calculate_stats(repl_df %>% filter(type_L_reach_H_cred==1), .x))
stats_pol_type_L_reach_L_cred <- map_df(beh_var, ~calculate_stats(repl_df %>% filter(type_L_reach_L_cred==1), .x))

stats_pol_ranking_1_100 <- map_df(beh_var, ~calculate_stats(repl_df %>% filter(ranking_cat == "1-100"), .x))
stats_pol_ranking_1_100$Type <- "1-100"

stats_pol_ranking_101_500 <- map_df(beh_var, ~calculate_stats(repl_df %>% filter(ranking_cat == "101-500"), .x))
stats_pol_ranking_101_500$Type <- "101-500"

stats_pol_ranking_501_1500 <- map_df(beh_var, ~calculate_stats(repl_df %>% filter(ranking_cat == "501-1500"), .x))
stats_pol_ranking_501_1500$Type <- "501-1500"

stats_pol_ranking_1501 <- map_df(beh_var, ~calculate_stats(repl_df %>% filter(ranking_cat == "1501+"), .x))
stats_pol_ranking_1501$Type <- "1501+"

stats_pol_is_US <- map_df(beh_var, ~calculate_stats(repl_df %>% filter(is_US==1), .x))
stats_pol_isnt_US <- map_df(beh_var, ~calculate_stats(repl_df %>% filter(is_US==0), .x))

stats_pol_us_users <- map_df(beh_var, ~calculate_stats(users_df %>% filter(is_bot_50==0), .x))

stats_pol_field <- bind_rows(
  mutate(stats_pol_is_humanities, Type = "Humanities"),
  mutate(stats_pol_is_soc_sci, Type = "Soc. Sciences"),
  mutate(stats_pol_is_stem, Type = "STEM")
)
stats_pol_field$Type <- factor(stats_pol_field$Type, levels = c("Humanities", "Soc. Sciences", "STEM"))

stats_pol_reach_by_cred <- bind_rows(
  mutate(stats_pol_type_H_reach_H_cred, Type = "High R-High C"),
  mutate(stats_pol_type_H_reach_L_cred, Type = "High R-Low C"),
  mutate(stats_pol_type_L_reach_H_cred, Type = "Low R-High C"),
  mutate(stats_pol_type_L_reach_L_cred, Type = "Low R-Low C")
)
stats_pol_reach_by_cred$Type <- factor(stats_pol_reach_by_cred$Type, levels = c("High R-High C", "High R-Low C", "Low R-High C", "Low R-Low C"))

stats_pol_gender <- bind_rows(
  mutate(stats_pol_is_female, Type = "Female"),
  mutate(stats_pol_is_male, Type = "Male")
)
stats_pol_gender$Type <- factor(stats_pol_gender$Type, levels = c("Female", "Male"))

stats_pol_rank <- bind_rows(
  stats_pol_ranking_1_100,
  stats_pol_ranking_101_500,
  stats_pol_ranking_501_1500,
  stats_pol_ranking_1501
)
stats_pol_rank$Type <- factor(stats_pol_rank$Type, levels = c("1-100", "101-500", "501-1500", "1501+"))

stats_pol_US <- bind_rows(
  mutate(stats_pol_is_US, Type = "US"),
  mutate(stats_pol_isnt_US, Type = "Non-US")
)
stats_pol_US$Type <- factor(stats_pol_US$Type, levels = c("US", "Non-US"))

stats_pol_main$Type <- "Main"
stats_pol_main$Type <- factor(stats_pol_main$Type, levels = "Main")

stats_pol_us_users$Type <- "US users"
stats_pol_us_users$Type <- factor(stats_pol_us_users$Type, levels = "US users")

stats_pol_main$Label <- factor(stats_pol_main$Term, levels = beh_var, labels = topic_label_mapping[beh_var])
stats_pol_field$Label <- factor(stats_pol_field$Term, levels = beh_var, labels = topic_label_mapping[beh_var])
stats_pol_reach_by_cred$Label <- factor(stats_pol_reach_by_cred$Term, levels = beh_var, labels = topic_label_mapping[beh_var])
stats_pol_gender$Label <- factor(stats_pol_gender$Term, levels = beh_var, labels = topic_label_mapping[beh_var])
stats_pol_rank$Label <- factor(stats_pol_rank$Term, levels = beh_var, labels = topic_label_mapping[beh_var])
stats_pol_US$Label <- factor(stats_pol_US$Term, levels = beh_var, labels = topic_label_mapping[beh_var])
stats_pol_us_users$Label <- factor(stats_pol_us_users$Term, levels = beh_var, labels = topic_label_mapping[beh_var])

stats_pol_comb <- bind_rows(stats_pol_main, stats_pol_field, stats_pol_reach_by_cred, stats_pol_gender, stats_pol_rank, stats_pol_US, stats_pol_us_users)

# Extract the US users values for each Term
us_users_values <- stats_pol_comb %>%
  filter(Type == "US users") %>%
  select(Term, Mean, StdError, CI_lower, CI_upper) %>%
  rename(US_users_Mean = Mean, US_users_StdError = StdError, US_users_CI_lower = CI_lower, US_users_CI_upper = CI_upper)

# Join the US users values with the original dataframe
stats_pol_comb <- stats_pol_comb %>%
  left_join(us_users_values, by = "Term") %>%
  mutate(
    Mean = Mean / US_users_Mean,
    StdError = StdError / US_users_StdError,
    CI_lower = CI_lower / US_users_CI_lower,
    CI_upper = CI_upper / US_users_CI_upper
  ) %>%
  select(Term, Type, Label, Mean, StdError, CI_lower, CI_upper)

stats_pol_comb %<>% filter(Type!="US users")

stats_pol_comb$Group <- with(stats_pol_comb, case_when(
  Type %in% c("Main") ~ "Main",
  Type %in% c("Female", "Male") ~ "Gender",
  Type %in% c("STEM", "Soc. Sciences", "Humanities") ~ "Fields",
  Type %in% c("High R-High C", "High R-Low C", "Low R-High C", "Low R-Low C") ~ "Reach (R) by Credibility (C)",
  Type %in% c("1-100", "101-500", "501-1500", "1501+") ~ "University Rankings",
  Type %in% c("US", "Non-US") ~ "Country",
  Type %in% c("US users") ~ "US General Twitter Users"
))
stats_pol_comb$Group <- factor(
  stats_pol_comb$Group,
  levels = c(
    "Main", 
    "Gender",
    "Fields",
    "Reach (R) by Credibility (C)",
    "University Rankings",
    "Country",
    "US General Twitter Users"
  )
)

# Ensure 'Type' has a proper order that reflects groupings
stats_pol_comb$Type <- factor(stats_pol_comb$Type, levels = c(
  "Main", "Female", "Male",
  "STEM", "Soc. Sciences", "Humanities",
  "High R-High C", "High R-Low C", "Low R-High C", "Low R-Low C",
  "1501+", "501-1500","101-500", "1-100",  
  "Non-US", "US",
  "US users"
))
# Color palette setup
color_values <- c(
  "Main" = "black",
  "Female" = "#E41A1C", "Male" = "#377EB8",
  "STEM" = "#4DAF4A", "Soc. Sciences" = "#FF7F00", "Humanities" = "#984EA3",
  "High R-High C" = "#A65628", "High R-Low C" = "#F781BF",
  "Low R-High C" = "#999999", "Low R-Low C" = "gold2",
  "1-100" = "#1F78B4", "101-500" = "#33A02C", "501-1500" = "#e31a1c", "1501+" = "#ff7f00",
  "US" = "red3", "Non-US" = "grey40",
  "US users"="purple3"
)

# Also map 'Label' correctly to factor
stats_pol_comb$Label <- factor(stats_pol_comb$Label, levels = unique(stats_pol_comb$Label))
  
stats_pol_comb$Label <- factor(
  stats_pol_comb$Label,
  levels = c("Egocentrism","Toxicity", "Emotionality/Reasoning")
)

# Calculate the 'Main' mean for each Label (facet column)
main_means <- stats_pol_comb %>%
  filter(Type == "Main") %>%
  group_by(Label) %>%
  summarize(Main_Mean = mean(Mean, na.rm = TRUE))

# Merge this back to the main dataset for plotting
stats_pol_comb <- stats_pol_comb %>%
  left_join(main_means, by = "Label")


# Adjusted Figure 4 plot
p_all_fig4 <- ggplot(stats_pol_comb %>% filter(Term %in% beh_var), aes(x = Mean, y = Type, color = Type, group = Type)) +
  # Conditional vertical lines based on Label
  geom_vline(data = stats_pol_comb %>% distinct(Label) %>% 
               mutate(xintercept = ifelse(Label == "Emotionality/Reasoning", 1, 0)),
             aes(xintercept = xintercept), linetype = "dotted", color = "grey99", size = 0.1, alpha = 0) +
  geom_vline(data = main_means, aes(xintercept = Main_Mean), linetype = "dotted", color = "grey60", size = 0.5) +
  geom_point(size = 2) +
  geom_errorbarh(aes(xmin = CI_lower, xmax = CI_upper), height = 0.2, size = 0.5) +
  scale_color_manual(values = color_values) +
  labs(x = "Mean Value", y = NULL) +
  theme_classic(base_size = 7) +
  theme(
    text = element_text(family = "Helvetica"),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    strip.text = element_text(face = "bold", size = 7),
    axis.text.x = element_text(size = 7, angle = 45, hjust = 1),
    axis.text.y = element_text(size = 7),
    legend.position = "none",
    strip.background = element_blank(),
    strip.placement = "outside",
    panel.spacing = unit(0.5, "lines")
  ) +
  facet_grid(rows = vars(Group), cols = vars(Label), scales = "free", space = "free_y", switch = "y")

# Save as EPS and PDF
ggsave("edf4.eps", p_all_fig4, width = 180 / 25.4, height = 180 / 25.4, device = cairo_ps)
ggsave("edf4.pdf", p_all_fig4, width = 180 / 25.4, height = 180 / 25.4, device = cairo_pdf)

```


# Reporting Statistical Evidence 

## Calculate the mean, standard deviation (SD), and 95% confidence intervals (CIs) for stance_cultural_liberalism and stance_econ_collectivism
```{r}
# Function to calculate mean, sd, and 95% CI
calculate_stats_base_r <- function(data, variable) {
  var_data <- data[[variable]]
  var_data <- var_data[!is.na(var_data)]
  
  mean_val <- mean(var_data)
  sd_val <- sd(var_data)
  
  # Sample size
  n <- length(var_data)
  
  # Standard error
  se_val <- sd_val / sqrt(n)
  
  # 95% confidence intervals
  error_margin <- qt(0.975, df = n - 1) * se_val
  ci_lower <- mean_val - error_margin
  ci_upper <- mean_val + error_margin
  
  list(
    mean = mean_val,
    sd = sd_val,
    ci_lower = ci_lower,
    ci_upper = ci_upper
  )
}

# Variables of interest
variables <- c("stance_climate_action", "pro_techno_prop", "pro_beh_prop")

# Calculate statistics for academics
cat("Academics:\n")
for (variable in variables) {
  stats <- calculate_stats_base_r(repl_df, variable)
  print(paste("Mean for", variable, ": ", stats$mean))
  print(paste("SD for", variable, ": ", stats$sd))
  print(paste("95% CI for", variable, ": (", stats$ci_lower, ", ", stats$ci_upper, ")"))
}


```


## Gender Differences in Climate Action, Techno-Optimism and Behavioral Adjustment
```{r}
# Function to calculate normality statistics
check_normality <- function(data, variable) {
  var_data <- data[[variable]]
  var_data <- var_data[!is.na(var_data)]
  
  skewness_val <- moments::skewness(var_data)
  kurtosis_val <- moments::kurtosis(var_data)
  
  list(
    skewness = skewness_val,
    kurtosis = kurtosis_val
  )
}

# Function to calculate variance homogeneity (Levene's Test)
check_variance_homogeneity <- function(data, variable, group_var) {
  combined_data <- data.frame(
    value = data[[variable]],
    group = factor(data[[group_var]])
  )
  
  levene_test <- car::leveneTest(value ~ group, data = combined_data)
  
  list(
    f_stat = levene_test$"F value"[1],
    df1 = levene_test$Df[1],
    df2 = levene_test$Df[2],
    p_value = levene_test$"Pr(>F)"[1]
  )
}

# Function for enhanced reporting
analyze_gender_differences <- function(data, variable, group_var) {
  # Normality checks
  normality_male <- check_normality(data %>% filter(!!sym(group_var) == 1), variable)
  normality_female <- check_normality(data %>% filter(!!sym(group_var) == 0), variable)
  
  # Variance homogeneity
  variance_check <- check_variance_homogeneity(data, variable, group_var)
  
  # Perform t-test
  t_test <- t.test(as.formula(paste(variable, "~", group_var)), data = data, var.equal = FALSE)
  
  # Calculate Cohen's d
  effect_size <- cohen.d(as.formula(paste(variable, "~", group_var)), data = data)
  
  # Group sample sizes
  n_male <- sum(data[[group_var]] == 1, na.rm = TRUE)
  n_female <- sum(data[[group_var]] == 0, na.rm = TRUE)
  
  # Return results
  list(
    normality_male = normality_male,
    normality_female = normality_female,
    variance_homogeneity = variance_check,
    t_test = list(
      t_stat = t_test$statistic,
      df = t_test$parameter,
      p_value = t_test$p.value,
      mean_diff = diff(t_test$estimate)
    ),
    cohen_d = effect_size$estimate,
    sample_sizes = list(male = n_male, female = n_female)
  )
}

# Variables to analyze
variables <- c("stance_climate_action", "pro_techno_prop", "pro_beh_prop")

# Analyze gender differences for each variable
for (variable in variables) {
  cat("=== Variable:", variable, "===\n")
  results <- analyze_gender_differences(repl_df, variable, "is_male")
  
  cat("Normality (Male): Skewness =", results$normality_male$skewness,
      ", Kurtosis =", results$normality_male$kurtosis, "\n")
  cat("Normality (Female): Skewness =", results$normality_female$skewness,
      ", Kurtosis =", results$normality_female$kurtosis, "\n")
  cat("Variance Homogeneity (Levene's Test): F(",
      results$variance_homogeneity$df1, ", ", results$variance_homogeneity$df2, ") = ",
      results$variance_homogeneity$f_stat, ", p =", results$variance_homogeneity$p_value, "\n")
  cat("T-test Results: t(", results$t_test$df, ") = ", results$t_test$t_stat,
      ", p =", results$t_test$p_value, ", Mean Difference = ", results$t_test$mean_diff, "\n")
  cat("Cohen's d:", results$cohen_d, "\n")
  cat("Sample Sizes: Male =", results$sample_sizes$male, ", Female =", results$sample_sizes$female, "\n\n")
}

```

## Field differences
```{r}
# 1) Construct a single factor variable field_group
df_fields <- repl_df %>%
  mutate(
    field_group = case_when(
      is_stem == 1 ~ "STEM",
      is_soc_sci == 1 ~ "Social Sciences",
      is_humanities == 1 ~ "Humanities",
      TRUE ~ NA_character_
    )
  ) %>%
  filter(!is.na(field_group))  # Exclude 'Other' or NA

# 2) Utility functions for normality, variance, t-test, etc.

# (a) Check normality: returns skewness and kurtosis
check_normality <- function(x) {
  x <- x[!is.na(x)]
  list(
    skewness = skewness(x),
    kurtosis = kurtosis(x)
  )
}

# (b) Levene's test for variance homogeneity, requires factor grouping
check_variance_homogeneity <- function(data, outcome, groupvar) {
  data_ok <- data %>%
    filter(!is.na(.data[[outcome]]), !is.na(.data[[groupvar]]))
  
  # Convert group to factor if not already
  data_ok[[groupvar]] <- factor(data_ok[[groupvar]], exclude = NULL)
  
  # Perform Levene's test
  levene_out <- leveneTest(as.formula(paste0(outcome, " ~ ", groupvar)), data = data_ok)
  
  list(
    f_value = levene_out$`F value`[1],
    df1 = levene_out$Df[1],
    df2 = levene_out$Df[2],
    p_value = levene_out$`Pr(>F)`[1]
  )
}

# (c) Compare two groups using Welch's t-test and Cohen's d
compare_two_groups <- function(data, outcome, groupvar, group1, group2) {
  # Subset data to just the two groups
  subdata <- data %>%
    filter(.data[[groupvar]] %in% c(group1, group2))
  
  # Normality
  normality_g1 <- check_normality(subdata[subdata[[groupvar]] == group1, outcome])
  normality_g2 <- check_normality(subdata[subdata[[groupvar]] == group2, outcome])
  
  # Levenes test
  levene_res <- check_variance_homogeneity(subdata, outcome, groupvar)
  
  # Welchs t-test (var.equal=FALSE is default)
  t_out <- t.test(
    as.formula(paste0(outcome, " ~ ", groupvar)),
    data = subdata,
    var.equal = FALSE
  )
  
  # Cohens d
  d_out <- cohen.d(
    as.formula(paste0(outcome, " ~ ", groupvar)),
    data = subdata
  )$estimate
  
  # Sample sizes
  n1 <- sum(subdata[[groupvar]] == group1)
  n2 <- sum(subdata[[groupvar]] == group2)
  
  # Collect results
  list(
    group1 = group1,
    group2 = group2,
    normality = list(
      group1 = normality_g1,
      group2 = normality_g2
    ),
    levene = levene_res,
    t_test = t_out,
    cohen_d = d_out,
    sample_sizes = c(group1 = n1, group2 = n2)
  )
}

# 3) Run pairwise comparisons among the 3 valid field_group levels
field_levels <- c("STEM", "Social Sciences", "Humanities")
pairs_list <- list(
  c("STEM", "Social Sciences"),
  c("STEM", "Humanities"),
  c("Social Sciences", "Humanities")
)

# 4) Choose variables to compare, e.g. stance_climate_action, pro_techno_prop, etc.
variables_to_compare <- c("stance_climate_action", "pro_techno_prop")

for (varname in variables_to_compare) {
  cat("=== Variable:", varname, "===\n\n")
  
  for (pair in pairs_list) {
    group1 <- pair[1]
    group2 <- pair[2]
    
    cat("--- Comparing", group1, "vs.", group2, "---\n")
    res <- compare_two_groups(
      data = df_fields,
      outcome = varname,
      groupvar = "field_group",
      group1 = group1,
      group2 = group2
    )
    
    # Print results
    # Normality
    cat(group1, "Normality: Skewness =", round(res$normality$group1$skewness, 3),
        ", Kurtosis =", round(res$normality$group1$kurtosis, 3), "\n")
    cat(group2, "Normality: Skewness =", round(res$normality$group2$skewness, 3),
        ", Kurtosis =", round(res$normality$group2$kurtosis, 3), "\n")
    
    # Levene's test
    cat("Levene's Test: F(", res$levene$df1, ",", res$levene$df2, ") =",
        round(res$levene$f_value, 2), ", p =", formatC(res$levene$p_value, format = "f", digits = 4), "\n")
    
    # Welch t-test
    t_st <- res$t_test$statistic
    t_df <- res$t_test$parameter
    t_pv <- res$t_test$p.value
    t_md <- res$t_test$estimate[1] - res$t_test$estimate[2]
    
    cat("T-test Results: t(", round(t_df, 1), ") =", round(t_st, 3),
        ", p =", formatC(t_pv, format = "f", digits = 4),
        ", Mean Difference =", round(t_md, 4), "\n")
    
    cat("Cohen's d:", round(res$cohen_d, 3), "\n")
    cat("Sample Sizes:", group1, "=", res$sample_sizes[1],
        ",", group2, "=", res$sample_sizes[2], "\n\n")
  }
}

```

## High vs Low Reach with Expertise
```{r}
# 1. Define helper functions
calc_descriptives <- function(x) {
  x <- x[!is.na(x)]
  n_val <- length(x)
  mean_val <- mean(x)
  sd_val <- sd(x)
  se_val <- sd_val / sqrt(n_val)
  crit_val <- qt(0.975, df = n_val - 1)
  ci_lower <- mean_val - crit_val * se_val
  ci_upper <- mean_val + crit_val * se_val
  list(n = n_val, mean = mean_val, sd = sd_val, ci_lower = ci_lower, ci_upper = ci_upper)
}

check_normality <- function(x) {
  x <- x[!is.na(x)]
  list(skewness = skewness(x), kurtosis = kurtosis(x))
}

check_variance_homogeneity <- function(x, g) {
  data_tmp <- data.frame(value = x, group = as.factor(g))
  data_tmp <- data_tmp[!is.na(data_tmp$value) & !is.na(data_tmp$group), ]  # Exclude missing values
  lev_out <- leveneTest(value ~ group, data = data_tmp)
  list(f_value = lev_out$`F value`[1], df1 = lev_out$Df[1], df2 = lev_out$Df[2], p_value = lev_out$`Pr(>F)`[1])
}

compare_groups <- function(data, outcome, group_var, group_val, ref_val) {
  # Filter for two groups
  subdata <- data %>%
    filter(!is.na(.data[[outcome]]) & !is.na(.data[[group_var]]) & 
             (.data[[group_var]] %in% c(group_val, ref_val)))
  
  group1 <- subdata[subdata[[group_var]] == group_val, outcome, drop = TRUE]
  group2 <- subdata[subdata[[group_var]] == ref_val, outcome, drop = TRUE]
  
  # Descriptive statistics
  desc1 <- calc_descriptives(group1)
  desc2 <- calc_descriptives(group2)
  
  # Normality
  norm1 <- check_normality(group1)
  norm2 <- check_normality(group2)
  
  # Levenes test
  levene_out <- check_variance_homogeneity(c(group1, group2), c(rep("Group1", length(group1)), rep("Group2", length(group2))))
  
  # Welchs t-test (default var.equal=FALSE)
  t_out <- t.test(group1, group2, var.equal = FALSE)
  
  # Cohens d
  d_out <- cohen.d(group1, group2, pooled = FALSE)$estimate
  
  list(
    group1_stats = desc1,
    group2_stats = desc2,
    normality = list(group1 = norm1, group2 = norm2),
    levene = levene_out,
    t_test = t_out,
    cohen_d = d_out
  )
}

# 2. Define groups and variables
variables <- c("stance_climate_action")
comparisons <- list(
  list(group = "type_H_reach_H_exp_climate", val = 1, ref = 0, label = "High-reach, high-credibility experts"),
  list(group = "type_H_reach_L_exp_climate", val = 1, ref = 0, label = "High-reach, low-credibility academics"),
  list(group = "type_L_reach_H_exp_climate", val = 1, ref = 0, label = "Low-reach, high-credibility experts")
)

# 3. Compare groups
for (varname in variables) {
  for (comp in comparisons) {
    res <- compare_groups(
      data = repl_df,
      outcome = varname,
      group_var = comp$group,
      group_val = comp$val,
      ref_val = comp$ref
    )
    
    cat("=== Comparing:", comp$label, "===\n")
    cat("Group 1: N =", res$group1_stats$n, "Mean =", round(res$group1_stats$mean, 4),
        "SD =", round(res$group1_stats$sd, 4), "95% CI = [", round(res$group1_stats$ci_lower, 4),
        ",", round(res$group1_stats$ci_upper, 4), "]\n")
    cat("Group 2: N =", res$group2_stats$n, "Mean =", round(res$group2_stats$mean, 4),
        "SD =", round(res$group2_stats$sd, 4), "95% CI = [", round(res$group2_stats$ci_lower, 4),
        ",", round(res$group2_stats$ci_upper, 4), "]\n")
    
    cat("Normality (Group 1): Skewness =", round(res$normality$group1$skewness, 3),
        ", Kurtosis =", round(res$normality$group1$kurtosis, 3), "\n")
    cat("Normality (Group 2): Skewness =", round(res$normality$group2$skewness, 3),
        ", Kurtosis =", round(res$normality$group2$kurtosis, 3), "\n")
    
    cat("Levenes Test: F(", res$levene$df1, ",", res$levene$df2, ") =", round(res$levene$f_value, 2),
        ", p =", formatC(res$levene$p_value, format = "f", digits = 4), "\n")
    
    cat("Welchs t-test: t(", round(res$t_test$parameter, 2), ") =", round(res$t_test$statistic, 3),
        ", p =", formatC(res$t_test$p.value, format = "f", digits = 4), ", Mean Diff =", round(res$t_test$estimate[1] - res$t_test$estimate[2], 4), "\n")
    cat("Cohens d:", round(res$cohen_d, 3), "\n\n")
  }
}

```


## Climate Action Stance: University Rankings;  US-based vs Non-US-based academics

```{r}
repl_df <- repl_df %>%
  mutate(is_top100 = ifelse(ranking_cat == "1-100", 1, 0),
         is_101_500 = ifelse(ranking_cat == "101-500", 1, 0),
         is_501_1500 = ifelse(ranking_cat == "501-1500", 1, 0),
         is_1501plus = ifelse(ranking_cat == "1501+", 1, 0))

# Function for detailed comparison
detailed_comparison <- function(data, outcome, groupvar, group1_label, group2_label) {
  # Subset data
  data_group1 <- data %>% filter(!!sym(groupvar) == 1)
  data_group2 <- data %>% filter(!!sym(groupvar) == 0)
  
  # Descriptive statistics
  n1 <- nrow(data_group1)
  n2 <- nrow(data_group2)
  mean1 <- mean(data_group1[[outcome]], na.rm = TRUE)
  mean2 <- mean(data_group2[[outcome]], na.rm = TRUE)
  sd1 <- sd(data_group1[[outcome]], na.rm = TRUE)
  sd2 <- sd(data_group2[[outcome]], na.rm = TRUE)
  ci1 <- t.test(data_group1[[outcome]])$conf.int
  ci2 <- t.test(data_group2[[outcome]])$conf.int
  
  # Normality checks
  skewness1 <- skewness(data_group1[[outcome]], na.rm = TRUE)
  kurtosis1 <- kurtosis(data_group1[[outcome]], na.rm = TRUE)
  skewness2 <- skewness(data_group2[[outcome]], na.rm = TRUE)
  kurtosis2 <- kurtosis(data_group2[[outcome]], na.rm = TRUE)
  
  # Levenes test for variance homogeneity
  combined_data <- data.frame(
    value = c(data_group1[[outcome]], data_group2[[outcome]]),
    group = c(rep(group1_label, n1), rep(group2_label, n2))
  )
  levene_result <- leveneTest(value ~ group, data = combined_data)
  
  # Welchs t-test
  ttest_result <- t.test(
    data_group1[[outcome]],
    data_group2[[outcome]],
    var.equal = FALSE
  )
  
  # Cohens d
  cohen_d_result <- cohen.d(
    data_group1[[outcome]], 
    data_group2[[outcome]]
  )
  
  # Print results
  cat("=== Comparison:", group1_label, "vs.", group2_label, "===\n")
  cat("Group 1 (", group1_label, "): N =", n1, 
      ", Mean =", round(mean1, 4), 
      ", SD =", round(sd1, 4), 
      ", 95% CI =", sprintf("[%.4f, %.4f]", ci1[1], ci1[2]), "\n")
  cat("Skewness =", round(skewness1, 3), ", Kurtosis =", round(kurtosis1, 3), "\n")
  
  cat("Group 2 (", group2_label, "): N =", n2, 
      ", Mean =", round(mean2, 4), 
      ", SD =", round(sd2, 4), 
      ", 95% CI =", sprintf("[%.4f, %.4f]", ci2[1], ci2[2]), "\n")
  cat("Skewness =", round(skewness2, 3), ", Kurtosis =", round(kurtosis2, 3), "\n")
  
  cat("Levenes Test: F(", levene_result$Df[1], ",", levene_result$Df[2], 
      ") =", round(levene_result$`F value`[1], 2), 
      ", p =", formatC(levene_result$`Pr(>F)`[1], format = "f", digits = 4), "\n")
  
  cat("Welchs t-test: t(", round(ttest_result$parameter, 2), 
      ") =", round(ttest_result$statistic, 3), 
      ", p =", formatC(ttest_result$p.value, format = "f", digits = 4), 
      ", Mean Diff =", round(ttest_result$estimate[1] - ttest_result$estimate[2], 4), "\n")
  
  cat("Cohens d:", round(cohen_d_result$estimate, 3), "\n\n")
}

# Climate Action: US vs Non-US
detailed_comparison(repl_df, "stance_climate_action", "is_US", "U.S.-based", "Non-U.S.-based")

# Behavioral Adjustments: US vs Non-US
detailed_comparison(repl_df, "pro_beh_prop", "is_US", "U.S.-based", "Non-U.S.-based")

# University Rankings: 1-100 vs 101-500
detailed_comparison(repl_df, "stance_climate_action", "is_top100", "Top 100 Universities", "101-500 Universities")

# University Rankings: 1-100 vs 501-1500
detailed_comparison(repl_df, "stance_climate_action", "is_501_1500", "Top 100 Universities", "501-1500 Universities")

# University Rankings: 1-100 vs 1501+
detailed_comparison(repl_df, "stance_climate_action", "is_1501plus", "Top 100 Universities", "1501+ Universities")

```


## Behavioral Adjustments Stance: High vs Low Reach with Expertise
```{r}
t.test(pro_beh_prop ~ type_H_reach_H_exp_climate, data = repl_df)
cohen.d(pro_beh_prop ~ type_H_reach_H_exp_climate, data = repl_df)

t.test(pro_beh_prop ~ type_H_reach_L_exp_climate, data = repl_df)
cohen.d(pro_beh_prop ~ type_H_reach_L_exp_climate, data = repl_df)

t.test(pro_beh_prop ~ type_L_reach_H_exp_climate, data = repl_df)
cohen.d(pro_beh_prop ~ type_L_reach_H_exp_climate, data = repl_df)

t.test(pro_beh_prop ~ type_L_reach_L_exp_climate, data = repl_df)
cohen.d(pro_beh_prop ~ type_L_reach_L_exp_climate, data = repl_df)

```

## Social Media Reach vs Expertise
```{r}
# High-reach non-experts (low expertise) vs high-reach experts on climate action stance
t.test(stance_climate_action ~ type_H_reach_H_exp_climate, data = repl_df %>% filter(type_H_reach_H_exp_climate == 1 | type_H_reach_L_exp_climate == 1))
cohen.d(stance_climate_action ~ type_H_reach_H_exp_climate, data = repl_df %>% filter(type_H_reach_H_exp_climate == 1 | type_H_reach_L_exp_climate == 1))

# Low-reach subject matter experts vs high-reach non-experts on climate action stance
t.test(stance_climate_action ~ type_L_reach_H_exp_climate, data = repl_df %>% filter(type_L_reach_H_exp_climate == 1 | type_H_reach_L_exp_climate == 1))
cohen.d(stance_climate_action ~ type_L_reach_H_exp_climate, data = repl_df %>% filter(type_L_reach_H_exp_climate == 1 | type_H_reach_L_exp_climate == 1))


```

## Calculate the mean, standard deviation (SD), and 95% confidence intervals (CIs) for stance_cultural_liberalism and stance_econ_collectivism
```{r}
# Function to calculate mean, sd, and 95% CI using base R
calculate_stats_base_r <- function(data, variable) {
  # Remove NA values
  var_data <- data[[variable]]
  var_data <- var_data[!is.na(var_data)]
  
  # Calculate mean and standard deviation
  mean_val <- mean(var_data)
  sd_val <- sd(var_data)
  
  # Sample size
  n <- length(var_data)
  
  # Standard error
  se_val <- sd_val / sqrt(n)
  
  # 95% confidence intervals
  error_margin <- qt(0.975, df = n - 1) * se_val
  ci_lower <- mean_val - error_margin
  ci_upper <- mean_val + error_margin
  
  # Return values as a named list
  list(
    mean = mean_val,
    sd = sd_val,
    ci_lower = ci_lower,
    ci_upper = ci_upper
  )
}

# Assuming your dataframe is called repl_df

# Calculate stats for stance_cultural_liberalism
cultural_liberalism_stats <- calculate_stats_base_r(repl_df, "stance_cultural_liberalism")
print(paste("Mean for Cultural Liberalism: ", cultural_liberalism_stats$mean))
print(paste("SD for Cultural Liberalism: ", cultural_liberalism_stats$sd))
print(paste("95% CI for Cultural Liberalism: (", cultural_liberalism_stats$ci_lower, ", ", cultural_liberalism_stats$ci_upper, ")"))

# Calculate stats for stance_econ_collectivism
econ_collectivism_stats <- calculate_stats_base_r(repl_df, "stance_econ_collectivism")
print(paste("Mean for Economic Collectivism: ", econ_collectivism_stats$mean))
print(paste("SD for Economic Collectivism: ", econ_collectivism_stats$sd))
print(paste("95% CI for Economic Collectivism: (", econ_collectivism_stats$ci_lower, ", ", econ_collectivism_stats$ci_upper, ")"))


```

Statistical tests for subgroup comparisons
```{r}
################################################################################
## HELPER FUNCTIONS
################################################################################

# (A) Normality check: returns skewness & kurtosis for a numeric vector
check_normality <- function(x) {
  x <- x[!is.na(x)]
  list(
    skewness = skewness(x),
    kurtosis = kurtosis(x)
  )
}

# (B) Levene's test for variance homogeneity
#     groupvar is a factor or will be coerced to factor
check_variance_homogeneity <- function(df, outcome, groupvar) {
  tmp <- df %>%
    filter(!is.na(.data[[outcome]]), !is.na(.data[[groupvar]]))
  
  tmp[[groupvar]] <- factor(tmp[[groupvar]])
  
  # `leveneTest` from the 'car' package
  lv_test <- leveneTest(as.formula(paste0(outcome, " ~ ", groupvar)), data = tmp)
  
  list(
    f_value = lv_test$`F value`[1],
    df1 = lv_test$Df[1],
    df2 = lv_test$Df[2],
    p_value = lv_test$`Pr(>F)`[1]
  )
}

# (C) Compare exactly two groups (binary factor) using Welchs t-test & Cohen's d
compare_two_groups <- function(df, outcome, groupvar, label_group1, label_group2) {
  # Filter out NAs
  sub_data <- df %>%
    filter(!is.na(.data[[outcome]]),
           !is.na(.data[[groupvar]])) %>%
    # keep only the two group levels of interest
    filter(.data[[groupvar]] %in% c(label_group1, label_group2))
  
  # Convert groupvar to factor
  sub_data[[groupvar]] <- factor(sub_data[[groupvar]])
  
  # Normality checks
  x_group1 <- sub_data[sub_data[[groupvar]] == label_group1, outcome, drop=TRUE]
  x_group2 <- sub_data[sub_data[[groupvar]] == label_group2, outcome, drop=TRUE]
  
  normality_g1 <- check_normality(x_group1)
  normality_g2 <- check_normality(x_group2)
  
  # Levene's test
  levene_res <- check_variance_homogeneity(sub_data, outcome, groupvar)
  
  # Welchs t-test
  t_res <- t.test(
    x = x_group1,
    y = x_group2,
    var.equal = FALSE  # Welch's by default
  )
  
  # Cohen's d
  d_res <- cohen.d(
    formula = as.formula(paste0(outcome, " ~ ", groupvar)),
    data = sub_data,
    pooled = FALSE  # by default, 'cohen.d' with factor does Hedge's correction
  )
  
  # Calculate sample sizes, means, CIs for each group
  n_g1 <- length(x_group1)
  n_g2 <- length(x_group2)
  mean_g1 <- mean(x_group1, na.rm = TRUE)
  mean_g2 <- mean(x_group2, na.rm = TRUE)
  sd_g1   <- sd(x_group1, na.rm = TRUE)
  sd_g2   <- sd(x_group2, na.rm = TRUE)
  
  # 95% CI for means
  # We do a simple approximate approach
  sem_g1 <- sd_g1 / sqrt(n_g1)
  sem_g2 <- sd_g2 / sqrt(n_g2)
  
  ci95_width_g1 <- qt(0.975, df=n_g1-1) * sem_g1
  ci95_width_g2 <- qt(0.975, df=n_g2-1) * sem_g2
  
  # Return a structured list
  list(
    group1_label = label_group1,
    group2_label = label_group2,
    
    sample_sizes = c(
      group1 = n_g1,
      group2 = n_g2
    ),
    
    normality = list(
      group1 = normality_g1,
      group2 = normality_g2
    ),
    
    variance_test = levene_res,
    
    # T-test results
    welch_t = list(
      statistic = t_res$statistic,
      df = t_res$parameter,
      p_value = t_res$p.value,
      mean_diff = (mean_g1 - mean_g2)
    ),
    
    # effect size
    cohen_d = d_res$estimate,  # or d_res$conf.int for CI
    
    # group descriptive stats
    group1_stats = list(
      mean = mean_g1,
      sd   = sd_g1,
      ci_lower = mean_g1 - ci95_width_g1,
      ci_upper = mean_g1 + ci95_width_g1
    ),
    group2_stats = list(
      mean = mean_g2,
      sd   = sd_g2,
      ci_lower = mean_g2 - ci95_width_g2,
      ci_upper = mean_g2 + ci95_width_g2
    )
  )
}

################################################################################
## High-Reach Experts vs Non-Experts for Cultural/Econ stances
################################################################################

# Example: High-reach, non-expert vs. High-reach, expert on Cultural Liberalism
res_cult_nonexpert_vs_expert <- compare_two_groups(
  df = repl_df,
  outcome = "stance_cultural_liberalism",
  groupvar = "type_H_reach_H_exp_cult",   # a 0/1 variable
  label_group1 = 0,  # e.g. "non-expert"
  label_group2 = 1   # e.g. "expert"
)
print(res_cult_nonexpert_vs_expert)

# Example: High-reach, non-expert vs. High-reach, expert on Economic Collectivism
res_econ_nonexpert_vs_expert <- compare_two_groups(
  df = repl_df,
  outcome = "stance_econ_collectivism",
  groupvar = "type_H_reach_H_exp_econ",
  label_group1 = 0, 
  label_group2 = 1
)
print(res_econ_nonexpert_vs_expert)

################################################################################
## Gender differences on Cultural/Econ stances
################################################################################

# Suppose is_male is 0/1
res_cult_male_vs_female <- compare_two_groups(
  df = repl_df,
  outcome = "stance_cultural_liberalism",
  groupvar = "is_male",
  label_group1 = 0,  # female
  label_group2 = 1   # male
)
print(res_cult_male_vs_female)

res_econ_male_vs_female <- compare_two_groups(
  df = repl_df,
  outcome = "stance_econ_collectivism",
  groupvar = "is_male",
  label_group1 = 0,
  label_group2 = 1
)
print(res_econ_male_vs_female)

################################################################################
## Field differences (Social Sci, Humanities, STEM) 
##    for Cultural/Econ stances
################################################################################

res_soc_sci_vs_others_cult <- compare_two_groups(
  df = repl_df,
  outcome = "stance_cultural_liberalism",
  groupvar = "is_soc_sci",
  label_group1 = 0, 
  label_group2 = 1
)
print(res_soc_sci_vs_others_cult)


res_stem_vs_others_cult <- compare_two_groups(
  df = repl_df,
  outcome = "stance_cultural_liberalism",
  groupvar = "is_stem",
  label_group1 = 0, 
  label_group2 = 1
)
print(res_stem_vs_others_cult)


res_humanities_vs_others_cult <- compare_two_groups(
  df = repl_df,
  outcome = "stance_cultural_liberalism",
  groupvar = "is_humanities",
  label_group1 = 0, 
  label_group2 = 1
)
print(res_humanities_vs_others_cult)


res_soc_sci_vs_others_econ <- compare_two_groups(
  df = repl_df,
  outcome = "stance_econ_collectivism",
  groupvar = "is_soc_sci",
  label_group1 = 0, 
  label_group2 = 1
)
print(res_soc_sci_vs_others_econ)


res_stem_vs_others_econ <- compare_two_groups(
  df = repl_df,
  outcome = "stance_econ_collectivism",
  groupvar = "is_stem",
  label_group1 = 0, 
  label_group2 = 1
)
print(res_stem_vs_others_econ)


res_humanities_vs_others_econ <- compare_two_groups(
  df = repl_df,
  outcome = "stance_econ_collectivism",
  groupvar = "is_humanities",
  label_group1 = 0, 
  label_group2 = 1
)
print(res_humanities_vs_others_econ)

################################################################################
##  University rankings and Cultural/Econ stances
################################################################################

res_top100_vs_101_500_cult <- compare_two_groups(
  df = repl_df %>% filter(ranking_cat %in% c("1-100","101-500")),
  outcome = "stance_cultural_liberalism",
  groupvar = "ranking_cat",
  label_group1 = "1-100",
  label_group2 = "101-500"
)
print(res_top100_vs_101_500_cult)


res_top100_vs_101_500_econ <- compare_two_groups(
  df = repl_df %>% filter(ranking_cat %in% c("1-100","101-500")),
  outcome = "stance_econ_collectivism",
  groupvar = "ranking_cat",
  label_group1 = "1-100",
  label_group2 = "101-500"
)
print(res_top100_vs_101_500_econ)

################################################################################
## U.S.-based vs Non-U.S. on Cultural/Econ stances
################################################################################

res_US_vs_nonUS_cult <- compare_two_groups(
  df = repl_df,
  outcome = "stance_cultural_liberalism",
  groupvar = "is_US",
  label_group1 = 0,   # Non-US
  label_group2 = 1    # US
)
print(res_US_vs_nonUS_cult)

res_US_vs_nonUS_econ <- compare_two_groups(
  df = repl_df,
  outcome = "stance_econ_collectivism",
  groupvar = "is_US",
  label_group1 = 0,
  label_group2 = 1
)
print(res_US_vs_nonUS_econ)

```

## Egocentrism
```{r}
################################################################################
## Statistical Comparisons for Egocentrism
################################################################################

# (A) Normality check: returns skewness & kurtosis for a numeric vector
check_normality <- function(x) {
  x <- x[!is.na(x)]
  list(
    skewness = skewness(x),
    kurtosis = kurtosis(x)
  )
}

# (B) Levene's test for variance homogeneity
check_variance_homogeneity <- function(df, outcome, groupvar) {
  tmp <- df %>%
    filter(!is.na(.data[[outcome]]), !is.na(.data[[groupvar]]))
  
  tmp[[groupvar]] <- factor(tmp[[groupvar]])
  
  # Levene's test using `leveneTest` from the 'car' package
  lv_test <- leveneTest(as.formula(paste0(outcome, " ~ ", groupvar)), data = tmp)
  
  list(
    f_value = lv_test$`F value`[1],
    df1 = lv_test$Df[1],
    df2 = lv_test$Df[2],
    p_value = lv_test$`Pr(>F)`[1]
  )
}

# (C) Compare two groups using Welchs t-test and Cohen's d
compare_two_groups <- function(df, outcome, groupvar, label_group1, label_group2) {
  sub_data <- df %>%
    filter(!is.na(.data[[outcome]]), !is.na(.data[[groupvar]])) %>%
    filter(.data[[groupvar]] %in% c(label_group1, label_group2))
  
  sub_data[[groupvar]] <- factor(sub_data[[groupvar]])
  
  x_group1 <- sub_data[sub_data[[groupvar]] == label_group1, outcome, drop = TRUE]
  x_group2 <- sub_data[sub_data[[groupvar]] == label_group2, outcome, drop = TRUE]
  
  # Normality checks
  normality_g1 <- check_normality(x_group1)
  normality_g2 <- check_normality(x_group2)
  
  # Levene's test
  levene_res <- check_variance_homogeneity(sub_data, outcome, groupvar)
  
  # Welchs t-test
  t_res <- t.test(
    x = x_group1,
    y = x_group2,
    var.equal = FALSE
  )
  
  # Cohen's d
  d_res <- cohen.d(
    formula = as.formula(paste0(outcome, " ~ ", groupvar)),
    data = sub_data,
    pooled = FALSE
  )
  
  # Group statistics
  n_g1 <- length(x_group1)
  n_g2 <- length(x_group2)
  mean_g1 <- mean(x_group1, na.rm = TRUE)
  mean_g2 <- mean(x_group2, na.rm = TRUE)
  sd_g1 <- sd(x_group1, na.rm = TRUE)
  sd_g2 <- sd(x_group2, na.rm = TRUE)
  
  ci_g1 <- c(
    mean_g1 - qt(0.975, df = n_g1 - 1) * (sd_g1 / sqrt(n_g1)),
    mean_g1 + qt(0.975, df = n_g1 - 1) * (sd_g1 / sqrt(n_g1))
  )
  
  ci_g2 <- c(
    mean_g2 - qt(0.975, df = n_g2 - 1) * (sd_g2 / sqrt(n_g2)),
    mean_g2 + qt(0.975, df = n_g2 - 1) * (sd_g2 / sqrt(n_g2))
  )
  
  list(
    group1_label = label_group1,
    group2_label = label_group2,
    sample_sizes = c(n_g1, n_g2),
    normality = list(group1 = normality_g1, group2 = normality_g2),
    variance_test = levene_res,
    t_test = t_res,
    cohen_d = d_res$estimate,
    group1_stats = list(mean = mean_g1, sd = sd_g1, ci = ci_g1),
    group2_stats = list(mean = mean_g2, sd = sd_g2, ci = ci_g2)
  )
}

################################################################################
## High Reach vs Low Credibility for Egocentrism
################################################################################

res_high_reach_low_cred <- compare_two_groups(
  df = repl_df,
  outcome = "egocentrism",
  groupvar = "type_H_reach_L_cred",
  label_group1 = 0,  # Others
  label_group2 = 1   # High reach, low credibility
)
print(res_high_reach_low_cred)

res_low_reach_high_cred <- compare_two_groups(
  df = repl_df,
  outcome = "egocentrism",
  groupvar = "type_L_reach_H_cred",
  label_group1 = 0,  # Others
  label_group2 = 1   # Low reach, high credibility
)
print(res_low_reach_high_cred)

################################################################################
## Field Differences for Egocentrism
################################################################################

res_humanities_vs_others <- compare_two_groups(
  df = repl_df,
  outcome = "egocentrism",
  groupvar = "is_humanities",
  label_group1 = 0, 
  label_group2 = 1
)
print(res_humanities_vs_others)

res_social_sciences_vs_others <- compare_two_groups(
  df = repl_df,
  outcome = "egocentrism",
  groupvar = "is_soc_sci",
  label_group1 = 0, 
  label_group2 = 1
)
print(res_social_sciences_vs_others)

################################################################################
## University Rankings for Egocentrism
################################################################################

res_top100_vs_101_500 <- compare_two_groups(
  df = repl_df %>% filter(ranking_cat %in% c("1-100", "101-500")),
  outcome = "egocentrism",
  groupvar = "ranking_cat",
  label_group1 = "1-100",
  label_group2 = "101-500"
)
print(res_top100_vs_101_500)

res_top100_vs_501_1500 <- compare_two_groups(
  df = repl_df %>% filter(ranking_cat %in% c("1-100", "501-1500")),
  outcome = "egocentrism",
  groupvar = "ranking_cat",
  label_group1 = "1-100",
  label_group2 = "501-1500"
)
print(res_top100_vs_501_1500)

################################################################################
## U.S.-based vs Non-U.S.-based for Egocentrism
################################################################################

res_US_vs_nonUS <- compare_two_groups(
  df = repl_df,
  outcome = "egocentrism",
  groupvar = "is_US",
  label_group1 = 0,  # Non-U.S.
  label_group2 = 1   # U.S.-based
)
print(res_US_vs_nonUS)

```

Calculate the mean, standard deviation (SD), and 95% confidence intervals (CIs) for Egocentrism
```{r}
# Function to calculate mean, sd, and 95% CI using base R
calculate_stats_base_r <- function(data, variable) {
  # Remove NA values
  var_data <- data[[variable]]
  var_data <- var_data[!is.na(var_data)]
  
  # Calculate mean and standard deviation
  mean_val <- mean(var_data)
  sd_val <- sd(var_data)
  
  # Sample size
  n <- length(var_data)
  
  # Standard error
  se_val <- sd_val / sqrt(n)
  
  # 95% confidence intervals
  error_margin <- qt(0.975, df = n - 1) * se_val
  ci_lower <- mean_val - error_margin
  ci_upper <- mean_val + error_margin
  
  # Return values as a named list
  list(
    mean = mean_val,
    sd = sd_val,
    ci_lower = ci_lower,
    ci_upper = ci_upper
  )
}

# Calculate stats for egocentrism
egocentrism_stats <- calculate_stats_base_r(repl_df, "egocentrism")
print(paste("Mean for Egocentrism: ", egocentrism_stats$mean))
print(paste("SD for Egocentrism: ", egocentrism_stats$sd))
print(paste("95% CI for Egocentrism: (", egocentrism_stats$ci_lower, ", ", egocentrism_stats$ci_upper, ")"))
```

## Toxicity 
```{r}
################################################################################
## Statistical Comparisons for Toxicity
################################################################################

# (A) Normality check: returns skewness & kurtosis for a numeric vector
check_normality <- function(x) {
  x <- x[!is.na(x)]
  list(
    skewness = skewness(x),
    kurtosis = kurtosis(x)
  )
}

# (B) Levene's test for variance homogeneity
check_variance_homogeneity <- function(df, outcome, groupvar) {
  tmp <- df %>%
    filter(!is.na(.data[[outcome]]), !is.na(.data[[groupvar]]))
  
  tmp[[groupvar]] <- factor(tmp[[groupvar]])
  
  # Levene's test using `leveneTest` from the 'car' package
  lv_test <- leveneTest(as.formula(paste0(outcome, " ~ ", groupvar)), data = tmp)
  
  list(
    f_value = lv_test$`F value`[1],
    df1 = lv_test$Df[1],
    df2 = lv_test$Df[2],
    p_value = lv_test$`Pr(>F)`[1]
  )
}

# (C) Compare two groups using Welchs t-test and Cohen's d
compare_two_groups <- function(df, outcome, groupvar, label_group1, label_group2) {
  sub_data <- df %>%
    filter(!is.na(.data[[outcome]]), !is.na(.data[[groupvar]])) %>%
    filter(.data[[groupvar]] %in% c(label_group1, label_group2))
  
  sub_data[[groupvar]] <- factor(sub_data[[groupvar]])
  
  x_group1 <- sub_data[sub_data[[groupvar]] == label_group1, outcome, drop = TRUE]
  x_group2 <- sub_data[sub_data[[groupvar]] == label_group2, outcome, drop = TRUE]
  
  # Normality checks
  normality_g1 <- check_normality(x_group1)
  normality_g2 <- check_normality(x_group2)
  
  # Levene's test
  levene_res <- check_variance_homogeneity(sub_data, outcome, groupvar)
  
  # Welchs t-test
  t_res <- t.test(
    x = x_group1,
    y = x_group2,
    var.equal = FALSE
  )
  
  # Cohen's d
  d_res <- cohen.d(
    formula = as.formula(paste0(outcome, " ~ ", groupvar)),
    data = sub_data,
    pooled = FALSE
  )
  
  # Group statistics
  n_g1 <- length(x_group1)
  n_g2 <- length(x_group2)
  mean_g1 <- mean(x_group1, na.rm = TRUE)
  mean_g2 <- mean(x_group2, na.rm = TRUE)
  sd_g1 <- sd(x_group1, na.rm = TRUE)
  sd_g2 <- sd(x_group2, na.rm = TRUE)
  
  ci_g1 <- c(
    mean_g1 - qt(0.975, df = n_g1 - 1) * (sd_g1 / sqrt(n_g1)),
    mean_g1 + qt(0.975, df = n_g1 - 1) * (sd_g1 / sqrt(n_g1))
  )
  
  ci_g2 <- c(
    mean_g2 - qt(0.975, df = n_g2 - 1) * (sd_g2 / sqrt(n_g2)),
    mean_g2 + qt(0.975, df = n_g2 - 1) * (sd_g2 / sqrt(n_g2))
  )
  
  list(
    group1_label = label_group1,
    group2_label = label_group2,
    sample_sizes = c(n_g1, n_g2),
    normality = list(group1 = normality_g1, group2 = normality_g2),
    variance_test = levene_res,
    t_test = t_res,
    cohen_d = d_res$estimate,
    group1_stats = list(mean = mean_g1, sd = sd_g1, ci = ci_g1),
    group2_stats = list(mean = mean_g2, sd = sd_g2, ci = ci_g2)
  )
}

################################################################################
## Field Differences for Toxicity
################################################################################

res_humanities_vs_others <- compare_two_groups(
  df = repl_df,
  outcome = "toxicity",
  groupvar = "is_humanities",
  label_group1 = 0, 
  label_group2 = 1
)
print(res_humanities_vs_others)

res_social_sciences_vs_others <- compare_two_groups(
  df = repl_df,
  outcome = "toxicity",
  groupvar = "is_soc_sci",
  label_group1 = 0, 
  label_group2 = 1
)
print(res_social_sciences_vs_others)

res_stem_vs_others <- compare_two_groups(
  df = repl_df,
  outcome = "toxicity",
  groupvar = "is_stem",
  label_group1 = 0, 
  label_group2 = 1
)
print(res_stem_vs_others)

################################################################################
## Reach and Credibility Differences for Toxicity
################################################################################

res_high_reach_low_cred <- compare_two_groups(
  df = repl_df,
  outcome = "toxicity",
  groupvar = "type_H_reach_L_cred",
  label_group1 = 0,  # Others
  label_group2 = 1   # High reach, low credibility
)
print(res_high_reach_low_cred)

res_low_reach_high_cred <- compare_two_groups(
  df = repl_df,
  outcome = "toxicity",
  groupvar = "type_L_reach_H_cred",
  label_group1 = 0,  # Others
  label_group2 = 1   # Low reach, high credibility
)
print(res_low_reach_high_cred)

################################################################################
## University Rankings for Toxicity
################################################################################

res_top100_vs_101_500 <- compare_two_groups(
  df = repl_df %>% filter(ranking_cat %in% c("1-100", "101-500")),
  outcome = "toxicity",
  groupvar = "ranking_cat",
  label_group1 = "1-100",
  label_group2 = "101-500"
)
print(res_top100_vs_101_500)

res_top100_vs_501_1500 <- compare_two_groups(
  df = repl_df %>% filter(ranking_cat %in% c("1-100", "501-1500")),
  outcome = "toxicity",
  groupvar = "ranking_cat",
  label_group1 = "1-100",
  label_group2 = "501-1500"
)
print(res_top100_vs_501_1500)

################################################################################
## U.S.-based vs Non-U.S.-based for Toxicity
################################################################################

res_US_vs_nonUS <- compare_two_groups(
  df = repl_df,
  outcome = "toxicity",
  groupvar = "is_US",
  label_group1 = 0,  # Non-U.S.
  label_group2 = 1   # U.S.-based
)
print(res_US_vs_nonUS)

```

Calculate Mean, SD, and 95% Confidence Intervals for Toxicity
```{r}
# Function to calculate mean, sd, and 95% CI using base R
calculate_stats_base_r <- function(data, variable) {
  var_data <- data[[variable]]
  var_data <- var_data[!is.na(var_data)]
  
  # Calculate mean and standard deviation
  mean_val <- mean(var_data)
  sd_val <- sd(var_data)
  
  # Sample size
  n <- length(var_data)
  
  # Standard error
  se_val <- sd_val / sqrt(n)
  
  # 95% confidence intervals
  error_margin <- qt(0.975, df = n - 1) * se_val
  ci_lower <- mean_val - error_margin
  ci_upper <- mean_val + error_margin
  
  # Return values as a named list
  list(
    mean = mean_val,
    sd = sd_val,
    ci_lower = ci_lower,
    ci_upper = ci_upper
  )
}

# Calculate stats for toxicity
toxicity_stats <- calculate_stats_base_r(repl_df, "toxicity")
print(paste("Mean for Toxicity: ", toxicity_stats$mean))
print(paste("SD for Toxicity: ", toxicity_stats$sd))
print(paste("95% CI for Toxicity: (", toxicity_stats$ci_lower, ", ", toxicity_stats$ci_upper, ")"))

```

## Emotionality

```{r}
################################################################################
## Statistical Comparisons for Emotionality-Reasoning
################################################################################

# (A) Normality check: returns skewness & kurtosis for a numeric vector
check_normality <- function(x) {
  x <- x[!is.na(x)]
  list(
    skewness = skewness(x),
    kurtosis = kurtosis(x)
  )
}

# (B) Levene's test for variance homogeneity
check_variance_homogeneity <- function(df, outcome, groupvar) {
  tmp <- df %>%
    filter(!is.na(.data[[outcome]]), !is.na(.data[[groupvar]]))
  
  tmp[[groupvar]] <- factor(tmp[[groupvar]])
  
  # Levene's test using `leveneTest` from the 'car' package
  lv_test <- leveneTest(as.formula(paste0(outcome, " ~ ", groupvar)), data = tmp)
  
  list(
    f_value = lv_test$`F value`[1],
    df1 = lv_test$Df[1],
    df2 = lv_test$Df[2],
    p_value = lv_test$`Pr(>F)`[1]
  )
}

# (C) Compare two groups using Welchs t-test and Cohen's d
compare_two_groups <- function(df, outcome, groupvar, label_group1, label_group2) {
  sub_data <- df %>%
    filter(!is.na(.data[[outcome]]), !is.na(.data[[groupvar]])) %>%
    filter(.data[[groupvar]] %in% c(label_group1, label_group2))
  
  sub_data[[groupvar]] <- factor(sub_data[[groupvar]])
  
  x_group1 <- sub_data[sub_data[[groupvar]] == label_group1, outcome, drop = TRUE]
  x_group2 <- sub_data[sub_data[[groupvar]] == label_group2, outcome, drop = TRUE]
  
  # Normality checks
  normality_g1 <- check_normality(x_group1)
  normality_g2 <- check_normality(x_group2)
  
  # Levene's test
  levene_res <- check_variance_homogeneity(sub_data, outcome, groupvar)
  
  # Welchs t-test
  t_res <- t.test(
    x = x_group1,
    y = x_group2,
    var.equal = FALSE
  )
  
  # Cohen's d
  d_res <- cohen.d(
    formula = as.formula(paste0(outcome, " ~ ", groupvar)),
    data = sub_data,
    pooled = FALSE
  )
  
  # Group statistics
  n_g1 <- length(x_group1)
  n_g2 <- length(x_group2)
  mean_g1 <- mean(x_group1, na.rm = TRUE)
  mean_g2 <- mean(x_group2, na.rm = TRUE)
  sd_g1 <- sd(x_group1, na.rm = TRUE)
  sd_g2 <- sd(x_group2, na.rm = TRUE)
  
  ci_g1 <- c(
    mean_g1 - qt(0.975, df = n_g1 - 1) * (sd_g1 / sqrt(n_g1)),
    mean_g1 + qt(0.975, df = n_g1 - 1) * (sd_g1 / sqrt(n_g1))
  )
  
  ci_g2 <- c(
    mean_g2 - qt(0.975, df = n_g2 - 1) * (sd_g2 / sqrt(n_g2)),
    mean_g2 + qt(0.975, df = n_g2 - 1) * (sd_g2 / sqrt(n_g2))
  )
  
  list(
    group1_label = label_group1,
    group2_label = label_group2,
    sample_sizes = c(n_g1, n_g2),
    normality = list(group1 = normality_g1, group2 = normality_g2),
    variance_test = levene_res,
    t_test = t_res,
    cohen_d = d_res$estimate,
    group1_stats = list(mean = mean_g1, sd = sd_g1, ci = ci_g1),
    group2_stats = list(mean = mean_g2, sd = sd_g2, ci = ci_g2)
  )
}


################################################################################
## Gender differences 
################################################################################

# Suppose is_male is 0/1
res_emotionality_male_vs_female <- compare_two_groups(
  df = repl_df,
  outcome = "emotionality",
  groupvar = "is_male",
  label_group1 = 0,  # female
  label_group2 = 1   # male
)
print(res_emotionality_male_vs_female)


################################################################################
## Field Differences for Emotionality-Reasoning
################################################################################

res_humanities_vs_others <- compare_two_groups(
  df = repl_df,
  outcome = "emotionality",
  groupvar = "is_humanities",
  label_group1 = 0, 
  label_group2 = 1
)
print(res_humanities_vs_others)

res_social_sciences_vs_others <- compare_two_groups(
  df = repl_df,
  outcome = "emotionality",
  groupvar = "is_soc_sci",
  label_group1 = 0, 
  label_group2 = 1
)
print(res_social_sciences_vs_others)

res_stem_vs_others <- compare_two_groups(
  df = repl_df,
  outcome = "emotionality",
  groupvar = "is_stem",
  label_group1 = 0, 
  label_group2 = 1
)
print(res_stem_vs_others)

################################################################################
## Reach and Credibility Differences for Emotionality-Reasoning
################################################################################

res_high_reach_low_cred <- compare_two_groups(
  df = repl_df,
  outcome = "emotionality",
  groupvar = "type_H_reach_L_cred",
  label_group1 = 0,  # Others
  label_group2 = 1   # High reach, low credibility
)
print(res_high_reach_low_cred)

res_low_reach_high_cred <- compare_two_groups(
  df = repl_df,
  outcome = "emotionality",
  groupvar = "type_L_reach_H_cred",
  label_group1 = 0,  # Others
  label_group2 = 1   # Low reach, high credibility
)
print(res_low_reach_high_cred)

################################################################################
## U.S.-based vs Non-U.S.-based for Emotionality-Reasoning
################################################################################

res_US_vs_nonUS <- compare_two_groups(
  df = repl_df,
  outcome = "emotionality",
  groupvar = "is_US",
  label_group1 = 0,  # Non-U.S.
  label_group2 = 1   # U.S.-based
)
print(res_US_vs_nonUS)

```

Calculate Mean, SD, and 95% Confidence Intervals for emotionality
```{r}
# Function to calculate mean, sd, and 95% CI for emotionality
calculate_stats_base_r <- function(data, variable) {
  var_data <- data[[variable]]
  var_data <- var_data[!is.na(var_data)]
  mean_val <- mean(var_data)
  sd_val <- sd(var_data)
  n <- length(var_data)
  se_val <- sd_val / sqrt(n)
  error_margin <- qt(0.975, df = n - 1) * se_val
  ci_lower <- mean_val - error_margin
  ci_upper <- mean_val + error_margin
  
  list(
    mean = mean_val,
    sd = sd_val,
    ci_lower = ci_lower,
    ci_upper = ci_upper
  )
}

# Calculate stats for emotionality
emotionality_stats <- calculate_stats_base_r(repl_df, "emotionality")
print(paste("Mean for Emotionality: ", emotionality_stats$mean))
print(paste("SD for Emotionality: ", emotionality_stats$sd))
print(paste("95% CI for Emotionality: (", emotionality_stats$ci_lower, ", ", emotionality_stats$ci_upper, ")"))
```





