---
title: "1_fig_1"
author: "Prashant Garg"
date: "2024-06-07"
output: html_document
---

# Goal: create Figure 1

----------------------------------------------------------------------

# Layperson Explanation:

Load Data: The script starts by loading the dataset from a CSV file into a dataframe.
Prepare Data for Zipf's Plot: The data is sorted and ranked by different metrics (statuses, favourites, followers, citations).
Separate Data for Ranks and Actual Values: The data is separated into two dataframes, one for ranks and one for actual values.
Melt Data for Ranks and Actual Values: The dataframes are melted to reshape them for plotting.
Adjust 'metric_type' for Better Readability: The levels of 'metric_type' are renamed for better readability in plots.
Merge Melted Data: The melted dataframes are merged into a single dataframe.
Filter Non-Finite Values: Non-finite values (e.g., infinite or NaN values) are removed from the dataframe.
Plot Zipf's Law: A ggplot is created to visualize Zipf's Law across different metrics, with points and a line of best fit.
Save Plot: The plot is saved as a high-resolution image file.

-----------------------------------------------------------------------
# Pseudocode:

# Load Data
LOAD dataset 'df_fig1.csv' into dataframe 'df_fig1'

# Prepare Data for Zipf's Plot
SORT 'df_fig1' by 'avg_statuses_count' in descending order
ASSIGN ranks to 'avg_statuses_count' as 'rank_statuses'
SORT 'df_fig1' by 'avg_favourites_count' in descending order
ASSIGN ranks to 'avg_favourites_count' as 'rank_favourites'
SORT 'df_fig1' by 'avg_followers_count' in descending order
ASSIGN ranks to 'avg_followers_count' as 'rank_followers'
SORT 'df_fig1' by 'cited_by_count' in descending order
ASSIGN ranks to 'cited_by_count' as 'rank_cited_by'

# Separate Data for Ranks and Actual Values
CREATE 'au_bal_ranks' with 'author_id', 'rank_statuses', 'rank_favourites', 'rank_followers', 'rank_cited_by'
CREATE 'au_bal_values' with 'author_id', 'avg_statuses_count', 'avg_favourites_count', 'avg_followers_count', 'cited_by_count'

# Melt Data for Ranks and Actual Values
MELT 'au_bal_ranks' into 'au_bal_ranks_melted' with 'author_id', 'metric_type', 'rank'
MELT 'au_bal_values' into 'au_bal_values_melted' with 'author_id', 'metric_type', 'actual_value'

# Adjust 'metric_type' for Better Readability
RENAME 'metric_type' levels in 'au_bal_ranks_melted' for readability
RENAME 'metric_type' levels in 'au_bal_values_melted' for readability

# Merge Melted Data
MERGE 'au_bal_ranks_melted' and 'au_bal_values_melted' into 'au_bal_merged' by 'author_id' and 'metric_type'

# Filter Non-Finite Values
REMOVE rows from 'au_bal_merged' where 'log(rank)' or 'log(actual_value)' is not finite

# Plot Zipf's Law
PLOT 'au_bal_merged' using ggplot2 with:
    - x-axis: log(rank)
    - y-axis: log(actual_value)
    - points colored black
    - line of best fit colored blue
    - labels: 'Log(Rank)', 'Log(Value)', 'Zipf's Law for Different Metrics'
    - facets: 'metric_type'

# Save Plot
SAVE plot 'zipplot' as 'fig1.jpg' with dpi=300, height=12, width=15
----------------------------------------------------------------------

# data load
df_fig1 contains individual level data from Twitter (follower count, favourites count and status count) and from OpenAlex (citation count).
```{r}
df_fig1 <- read_csv( "../2_data/df_fig1.csv")
```


# Prepare data for Zipfs plot
```{r}
# Rank the data for each metric and prepare for plotting
au_bal_ranked <- df_fig1 %>%
  arrange(desc(avg_statuses_count)) %>%
  mutate(rank_statuses = row_number()) %>%
  arrange(desc(avg_favourites_count)) %>%
  mutate(rank_favourites = row_number()) %>%
  arrange(desc(avg_followers_count)) %>%
  mutate(rank_followers = row_number()) %>%
  arrange(desc(cited_by_count)) %>%
  mutate(rank_cited_by = row_number())

# Separate the data for ranks and actual values
au_bal_ranks <- au_bal_ranked %>%
  select(author_id, rank_statuses, rank_favourites, rank_followers, rank_cited_by)

au_bal_values <- au_bal_ranked %>%
  select(author_id, avg_statuses_count, avg_favourites_count, avg_followers_count, cited_by_count)

# Melt the data for ranks and actual values
au_bal_ranks_melted <- melt(au_bal_ranks, 
                            id.vars = "author_id", 
                            variable.name = "metric_type", 
                            value.name = "rank")

au_bal_values_melted <- melt(au_bal_values, 
                             id.vars = "author_id", 
                             variable.name = "metric_type", 
                             value.name = "actual_value")

# Adjust metric_type for better readability in both melted data tables
au_bal_ranks_melted$metric_type <- factor(au_bal_ranks_melted$metric_type,
                                          levels = c("rank_statuses", "rank_favourites", "rank_followers", "rank_cited_by"),
                                          labels = c("Content Creation (Posts)", "Engagement\ (Likes Received)", "Public Reach (Followers)", "Citations Count"))

au_bal_values_melted$metric_type <- factor(au_bal_values_melted$metric_type,
                                           levels = c("avg_statuses_count", "avg_favourites_count", "avg_followers_count", "cited_by_count"),
                                           labels = c("Content Creation (Posts)", "Engagement (Likes Received)", "Public Reach (Followers)", "Citations Count"))

# Merge the melted data for ranks and actual values
au_bal_merged <- merge(au_bal_ranks_melted, au_bal_values_melted, by = c("author_id", "metric_type"))

# Remove non-finite values
au_bal_merged <- au_bal_merged %>%
  filter(is.finite(log(rank)), is.finite(log(actual_value)))
```

# Plot 
```{r}
# Plot using ggplot2 with facets
zipplot <- ggplot(au_bal_merged, aes(x = log(rank), y = log(actual_value))) +
  geom_point(alpha = 0.6, aes(color = "Point")) +
  geom_smooth(method = "lm", se = FALSE, aes(color = "Line")) +
  labs(x = "Log(Rank)", y = "Log(Value)", title = "Zipf's Law for Different Metrics") +
  facet_wrap(~metric_type, ncol = 2) +
  # ggthemes::theme_tufte(base_size = 30) +
  theme_classic(base_size = 30) +
  theme(
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    plot.title = element_blank(),
    strip.text = element_text(face = "bold"),
    legend.position = "bottom"
  ) +
  scale_color_manual(
    name = NULL,
    values = c("Point" = "black", "Line" = "blue"),
    labels = c("Point" = "Actual Distribution", "Line" = "Zipf Distribution")
  )+
  guides(color = guide_legend(override.aes = list(size = 5)))

zipplot
```

# Save
optionally, save the plot to view it clearly as it appears in the paper
```{r}
# Save the plot
ggsave(filename = "fig1.jpg", plot = zipplot, dpi = 300, height = 12, width = 15)

```

